---
title: "22q fMRI analysis"
author: "C. Schleifer"
date: "2022-09-30"
output: html_document
---

# setup workspace
```{r setup, message=FALSE, warning=FALSE, paged.print=FALSE}
# function to set up environment
# clear workspace
rm(list = ls(all.names = TRUE))

# use SSHFS to mount hoffman2 server (download SSHFS for mac: https://osxfuse.github.io/)
# TODO: set hoffman2 username
uname <- "schleife"
# set local path to mount server
hoffman <- "~/Desktop/hoffman_mount"
# create directory if needed 
# if(!file.exists(hoffman)){dir.create(hoffman)}
# make string to run as system command
mntcommand <- paste0("umount -f ", hoffman,"; sshfs ",uname,"@hoffman2.idre.ucla.edu:/u/project/cbearden/data ",hoffman)
# if hoffman directory is empty, use system command and sshfs to mount server, if not empty assume already mounted and skip
if(length(list.files(hoffman)) == 0){system(mntcommand)}else{print(paste(hoffman,"is not empty...skipping SSHFS step"))}

# list packages to load
packages <- c("devtools","conflicted","here","magrittr", "dplyr", "tidyr","readxl", "ggplot2","gghalves","patchwork", "ggrepel", "ggpubr", "gt", "scico", "RColorBrewer", "ciftiTools", "tableone", "data.table", "reshape2", "neuroCombat", "pls")

# install packages if not yet installed
all_packages <- rownames(installed.packages())
installed_packages <- packages %in% all_packages
if (any(installed_packages == FALSE)){install.packages(packages[!installed_packages])}

# load packages
invisible(lapply(packages, library, character.only = TRUE))

# install neuroComBat from github 
# https://github.com/Jfortin1/neuroCombat_Rpackage
#install_github("jfortin1/neuroCombatData")
#install_github("jfortin1/neuroCombat_Rpackage")

# use the filter function from dplyr, not stats
conflict_prefer("filter", "dplyr")

# get path to project repo directory
project <- here()
print(paste("Project directory:", project))

# set up connectome workbench path for ciftiTools
# https://www.humanconnectome.org/software/get-connectome-workbench
# local wbpath (edit this path if workbench is installed in another location, e.g. on hoffman: /u/project/CCN/apps/hcp/current/workbench/bin_rh_linux64/)
# TODO: edit if necessary
wbpath <- "/Applications/workbench/bin_macosx64/"
ciftiTools.setOption("wb_path", wbpath)

# load rgl for ciftiTools visualization
# may require XQartz v2.8.1 to be installed locally
if(!require('rgl', quietly=TRUE)){install.packages('rgl')}
rgl::setupKnitr()
rgl::rgl.open(); rgl::rgl.close()

# set to TRUE to save outputs, otherwise won't save
save_outputs=FALSE

# load Rdata instead of loading individual files
# load(file.path(project,"demographics/22q_chr_fmri_init.Rdata"))
# load(file.path(project,"git_exclude/22q_chr_fmri_main.Rdata"))
# load(file.path(project,"git_exclude/22q_chr_fmri_full_R1.Rdata"))
```

get subject IDs and load demographic data
```{r loadDemo}
# load CAB-NP network parcellation
# https://github.com/ColeLab/ColeAnticevicNetPartition
ji_key <- read.table(file.path(project,"CAB-NP/CortexSubcortex_ColeAnticevic_NetPartition_wSubcorGSR_parcels_LR_LabelKey.txt"),header=T)
ji_net_keys <- ji_key[,c("NETWORKKEY","NETWORK")] %>% distinct %>% arrange(NETWORKKEY)
# read cifti with subcortical structures labeled 
xii_Ji_parcel <- read_cifti(file.path(project,"CAB-NP/CortexSubcortex_ColeAnticevic_NetPartition_wSubcorGSR_parcels_LR.dscalar.nii"), brainstructures = "all")
xii_Ji_network <- read_cifti(file.path(project,"CAB-NP/CortexSubcortex_ColeAnticevic_NetPartition_wSubcorGSR_netassignments_LR.dscalar.nii"), brainstructures = "all")
# read only surface parcels
xii_Ji_parcel_surf <- read_cifti(file.path(project,"CAB-NP/CortexSubcortex_ColeAnticevic_NetPartition_wSubcorGSR_parcels_LR.dscalar.nii"), brainstructures = c("left", "right"))

# paths to sessions directories
trio_dir <- file.path(hoffman,"22q/qunex_studyfolder/sessions")
prisma_dir <- file.path(hoffman,"22qPrisma/qunex_studyfolder/sessions")
suny_dir <- file.path(hoffman,"Enigma/SUNY/qunex_studyfolder/sessions")
rome_dir <- file.path(hoffman,"Enigma/Rome/qunex_studyfolder/sessions")
iop_dir <- file.path(hoffman,"Enigma/IoP/qunex_studyfolder/sessions")
napls_dir <- file.path(hoffman,"NAPLS_BOLD/NAPLS2/sessions/S_sessions/")

# get list of sessions
trio_sessions <- list.files(trio_dir,pattern="Q_[0-9]")
trio_sessions <- c("Q_0001_09242012", "Q_0001_10152010", "Q_0005_04182011", "Q_0007_04012011", "Q_0009_09292011", "Q_0016_03292011", "Q_0016_10082012", "Q_0020_03262012", "Q_0020_05052011", "Q_0021_01132011", "Q_0021_11052012", "Q_0024_04152011", "Q_0024_09212012", "Q_0026_03232012", "Q_0026_05032013", "Q_0033_03192010", "Q_0036_03302010", "Q_0036_06212012", "Q_0036_06282011", "Q_0037_04202011", "Q_0038_06042010", "Q_0039_04132010", "Q_0039_06012011", "Q_0041_09262012", "Q_0045_07132010", "Q_0045_08302011", "Q_0045_10052012", "Q_0051_01302012", "Q_0052_07302010", "Q_0053_08022010", "Q_0053_12212012", "Q_0054_08062010", "Q_0056_08252010", "Q_0056_09102012", "Q_0059_08032011", "Q_0062_11302011", "Q_0076_10212010", "Q_0077_02292012", "Q_0077_03112013", "Q_0077_10252010", "Q_0078_11102011", "Q_0080_11222010", "Q_0081_11242010", "Q_0082_01062012", "Q_0082_01112013", "Q_0082_12162010", "Q_0085_02242012", "Q_0091_03052012", "Q_0091_03072011", "Q_0092_03102011", "Q_0093_03082011", "Q_0093_03122012", "Q_0093_03122013", "Q_0098_04012011", "Q_0099_04012011", "Q_0100_04082011", "Q_0101_01032013", "Q_0101_04122011", "Q_0102_01032013", "Q_0102_04122011", "Q_0103_04182011", "Q_0103_08272012", "Q_0105_05022011", "Q_0109_05262011", "Q_0112_11142012", "Q_0114_11092012", "Q_0117_07062011", "Q_0117_08312012", "Q_0118_07072011", "Q_0124_07292011", "Q_0124_09172012", "Q_0127_03052013", "Q_0127_08012014", "Q_0127_08082011", "Q_0130_08132012", "Q_0130_08162011", "Q_0130_11042014", "Q_0132_08222011", "Q_0135_09012011", "Q_0141_10072013", "Q_0141_10092012", "Q_0146_11082012", "Q_0146_12072011", "Q_0147_08112015", "Q_0147_08142014", "Q_0147_12122011", "Q_0149_11192012", "Q_0149_12192011", "Q_0150_11192012", "Q_0150_12202011", "Q_0151_01122012", "Q_0153_01202012", "Q_0156_01312012", "Q_0156_12102013", "Q_0157_01312012", "Q_0159_02122013", "Q_0161_03012012", "Q_0161_04192013", "Q_0162_03202012", "Q_0163_03262012", "Q_0166_01092014", "Q_0166_04052012", "Q_0168_04052012", "Q_0169_04062012", "Q_0170_04102012", "Q_0170_11252014", "Q_0171_04102012", "Q_0171_11252014", "Q_0172_04122012", "Q_0172_04262013", "Q_0173_04122012", "Q_0173_04172014", "Q_0173_04262013", "Q_0174_04182012", "Q_0174_04272015", "Q_0176_04242012", "Q_0176_05072013", "Q_0177_05012012", "Q_0178_05012012", "Q_0182_05182012", "Q_0184_05242012", "Q_0185_05242012", "Q_0186_04092015", "Q_0188_05242012", "Q_0189_05242012", "Q_0190_06012012", "Q_0190_08132013", "Q_0196_06192015", "Q_0196_06202012", "Q_0196_09122013", "Q_0200_04032015", "Q_0200_08052013", "Q_0213_08032012", "Q_0215_08062012", "Q_0215_08172015", "Q_0216_08062012", "Q_0216_08172015", "Q_0217_01142014", "Q_0217_02042015", "Q_0217_08092012", "Q_0219_08122014", "Q_0219_08162012", "Q_0219_09012015", "Q_0222_08212012", "Q_0223_08212012", "Q_0227_10032012", "Q_0228_01292014", "Q_0228_09272012", "Q_0229_10022012", "Q_0232_12122012", "Q_0234_03252014", "Q_0234_12132012", "Q_0236_03072013", "Q_0238_03202013", "Q_0238_08042014", "Q_0238_11132015", "Q_0240_03232015", "Q_0240_03272013", "Q_0240_06262014", "Q_0242_03272013", "Q_0242_05162016", "Q_0244_09162013", "Q_0244_09232014", "Q_0246_09242013", "Q_0252_12102013", "Q_0255_10212014", "Q_0260_06092014", "Q_0260_10262015", "Q_0266_08122014", "Q_0268_10132014", "Q_0269_10142014", "Q_0277_12082014", "Q_0284_03182015", "Q_0285_03182015", "Q_0286_03182015", "Q_0291_04172015", "Q_0307_10132015", "Q_0310_11182015", "Q_0311_12082015", "Q_0315_01262016", "Q_0321_03232016", "Q_0322_03312016", "Q_0326_04142016", "Q_0327_04142016")
#prisma_sessions <- list.files(prisma_dir,pattern="Q_[0-9]")
prisma_sessions <- c("Q_0005_11072017", "Q_0017_10022017", "Q_0019_03022020", "Q_0036_08082017", "Q_0036_08312018", "Q_0036_09302019", "Q_0037_08152017", "Q_0041_10092017", "Q_0051_02032017", "Q_0105_03112020", "Q_0105_12032018", "Q_0114_12052017", "Q_0141_06122018", "Q_0141_08052019", "Q_0147_12112017", "Q_0147_12112018", "Q_0196_01082020", "Q_0213_05012017", "Q_0217_01242017", "Q_0217_02192020", "Q_0235_05252017", "Q_0238_02202018", "Q_0240_09192017", "Q_0240_11162018", "Q_0246_10092018", "Q_0246_10102017", "Q_0246_10142016", "Q_0260_06192017", "Q_0260_06242019", "Q_0260_06252018", "Q_0263_02252019", "Q_0263_02262018", "Q_0263_11072016", "Q_0271_10182016", "Q_0277_12132016", "Q_0278_11292017", "Q_0279_11302017", "Q_0279_12052019", "Q_0279_12132016", "Q_0285_03212017", "Q_0285_06062018", "Q_0286_03212017", "Q_0287_06062018", "Q_0289_03212017", "Q_0289_06062018", "Q_0291_11042016", "Q_0291_11302018", "Q_0304_12202016", "Q_0310_01252018", "Q_0310_02132017", "Q_0310_04292019", "Q_0319_03192018", "Q_0319_03282017", "Q_0321_03192018", "Q_0321_03272017", "Q_0324_04182018", "Q_0326_10202017", "Q_0326_12062018", "Q_0327_10192017", "Q_0327_12072018", "Q_0331_06102019", "Q_0331_06212018", "Q_0331_06272017", "Q_0333_04142017", "Q_0334_12012016", "Q_0336_01102017", "Q_0345_04122017", "Q_0345_08152018", "Q_0345_09112019", "Q_0346_04102017", "Q_0346_04102018", "Q_0348_04212017", "Q_0348_08152018", "Q_0350_04192017", "Q_0350_09142018", "Q_0353_04182018", "Q_0353_05022017", "Q_0355_05312018", "Q_0356_05312018", "Q_0361_10212019", "Q_0361_11202018", "Q_0369_04182018", "Q_0369_06182019", "Q_0371_08042020", "Q_0374_05252018", "Q_0381_08072018", "Q_0381_09102019", "Q_0382_08282018", "Q_0383_08282018", "Q_0387_08242018", "Q_0387_12032019", "Q_0390_09042018", "Q_0390_09302019", "Q_0391_09252018", "Q_0395_11062018", "Q_0397_10172019", "Q_0402_01112019", "Q_0404_03112019", "Q_0407_06122019", "Q_0408_05172019", "Q_0414_07172019", "Q_0415_07292019", "Q_0416_07292019", "Q_0425_11052019", "Q_0429_01092020", "Q_0432_02142020", "Q_0433_02262020", "Q_0443_06282021", "Q_0446_06152021", "Q_0459_08192021", "Q_0461_09112021", "Q_0484_01042022", "Q_0519_05312022", "Q_0520_06012022", "Q_0521_05202022", "Q_0525_06072022", "Q_0526_06242022", "Q_0527_07112022", "Q_0528_07202022", "Q_0529_07202022", "Q_0561_11032022", "Q_0568_10252022")
# exclude Q_0390_09302019 for now due to no AP BOLD, and exclude two NAPLS subjects with no demographic info and 02_S0013_00 with some NAs in NetHo data (need to investigate further)
# exclude the following NAPLS sessions after T1w QC (12/11/23)
# 04_S0115_00
# 06_S0068_00
# 01_S0040_00
# 01_S0045_03
# 08_S0052_00
# 01_S0064_00
# 01_S0072_00
# 04_S0115_00
# 08_S0052_00
# 01_S0064_00
exclude_sessions <- c("Q_0390_09302019","01_S0083_00","01_S0128_00","02_S0013_00","04_S0115_00","06_S0068_00","01_S0040_00","01_S0045_03","08_S0052_00","01_S0064_00","01_S0072_00","04_S0115_00","08_S0052_00","01_S0064_00")

# for now also exclude several new sessions without rsfa calculated
#exclude_sessions <- c("Q_0214_05012017","Q_0390_09302019","Q_0477_01052022","Q_0484_01042022","Q_0508_06232022","Q_0519_05312022","Q_0520_06012022","Q_0521_05202022","Q_0525_06072022","Q_0526_06242022","Q_0527_07112022","Q_0528_07202022","Q_0529_07202022","Q_0541_07182022","Q_0549_10182022","Q_0561_11032022","Q_0568_10252022")
prisma_sessions <- prisma_sessions[! prisma_sessions %in% exclude_sessions]
suny_sessions <- list.files(suny_dir,pattern="X[0-9]")
iop_sessions <- list.files(iop_dir,pattern="GQAIMS[0-9]")
rome_sessions <- c(list.files(rome_dir, pattern="C[0-9]"),list.files(rome_dir, pattern="D[0-9]"))
#napls_sessions <- list.files(napls_dir,pattern="[0-9]_")
# get only baseline napls
napls_sessions <- list.files(napls_dir,pattern="_00$")
napls_sessions <- napls_sessions[! napls_sessions %in% exclude_sessions]

all_sessions <- c(trio_sessions,prisma_sessions,suny_sessions,rome_sessions,iop_sessions, napls_sessions)

# read multisite demo table
#demo_multisite <- read.csv(file.path(project,"demographics/multisite/22q_multisite_demo_f31.csv"))
demo_multisite <- read.csv(file.path(project,"demographics/multisite/22q_multisite_demo.csv"))
# exclude listed sessions if any are in list
#demo_multisite <- demo_multisite[! demo_multisite$MRI_S_ID %in% exclude_sessions,]
# include only subject with mri
demo_multisite <- filter(demo_multisite, MRI_S_ID %in% all_sessions)
# subset to baseline
demo_multisite_bl <- filter(demo_multisite, visit_index==1)
# filter age
demo_multisite_bl <- filter(demo_multisite_bl, AGE >= 8 & AGE <= 45)

# read NAPLS baseline demographics
demo_napls_bl <- read.csv(file.path(project,"demographics/NAPLS/NAPLS_ClientInfo_13Jan2016nocommas.csv"))
# match napls MRI_S_IDs to demo table
napls_id_split <- strsplit(napls_sessions, split="_") %>% do.call(rbind,.) %>% as.data.frame
napls_id_split$MRI_S_ID <- napls_sessions
napls_id_bl <- filter(napls_id_split, V3=="00")
napls_id_match <- data.frame(MRI_S_ID=napls_id_bl$MRI_S_ID, SiteNumber=as.numeric(napls_id_bl$V1), SubjectNumber=as.numeric(gsub("S","",napls_id_bl$V2)))
# merge with demo
demo_napls_id <- merge(x=demo_napls_bl, y=napls_id_match, by=c("SiteNumber","SubjectNumber"), all.y=TRUE)

# make df with basic demographics across all 22q and NAPLS
# first add napls data
demo_napls=data.frame(MRI_S_ID=demo_napls_id$MRI_S_ID,
                      Group=demo_napls_id$SubjectType,
                      AGE=demo_napls_id$demo_age_ym,
                      SEX=demo_napls_id$demo_sex,
                      Site=demo_napls_id$SiteNumber)
demo_napls$Site <- paste0("NAPLS",demo_napls$Site)
demo_napls$SEX <-  factor(demo_napls$SEX,levels=c(1,2),labels=c("M","F"))
demo_napls$Group <- factor(demo_napls$Group,levels=c("Prodromal","Control"),labels=c("CHR","CONTROL-N"))
# then add 22q data
demo_22q=data.frame(MRI_S_ID=demo_multisite_bl$MRI_S_ID,
                      Group=demo_multisite_bl$SUBJECT_IDENTITY,
                      AGE=demo_multisite_bl$AGE,
                      SEX=demo_multisite_bl$SEX,
                      Site=demo_multisite_bl$Site)
demo_22q$SEX <-  factor(demo_22q$SEX,levels=c("M","F"),labels=c("M","F"))
demo_22q$Group <- factor(demo_22q$Group,levels=c("PATIENT-DEL","CONTROL"),labels=c("22qDel","CONTROL"))
# combine
demo_22q_napls <- rbind(demo_22q, demo_napls)
# get age squared column for regression
demo_22q_napls$AGE2 <- (demo_22q_napls$AGE)^2
```

add converter label for NAPLS2
```{r convertLabel}
converters <- read_xlsx(file.path(project,"demographics/NAPLS/converters.xlsx"))
convert_ids <- merge(x=converters, y=napls_id_match, by=c("SiteNumber","SubjectNumber"))
demo_22q_napls$GroupConvert <- as.character(demo_22q_napls$Group)
demo_22q_napls[which(demo_22q_napls$MRI_S_ID %in% convert_ids$MRI_S_ID),"GroupConvert"] <- "CHRc"
demo_22q_napls$GroupConvert %<>% as.factor
```

load movement data
```{r loadMovement}
## get movement info
# function to get mapping between boldn and run name from session_hcp.txt
get_boldn_names <- function(sesh,sessions_dir){
  hcptxt <- read.table(file.path(sessions_dir,sesh,"session_hcp.txt"),sep=":",comment.char="#",fill=T,strip.white=T,col.names=c(1:4)) %>% as.data.frame()
  hcpbolds <- hcptxt %>% filter(grepl("bold[0-9]",X2))
  df_out <- cbind(rep(sesh,times=nrow(hcpbolds)),hcpbolds$X2,hcpbolds$X3)
  colnames(df_out) <- c("sesh","bold_n","bold_name")
  return(df_out)
}

# function to get %udvarsme from images/functional/movement/boldn.scrub
get_percent_udvarsme <- function(sesh,sessions_dir,bold_name_use){
  mov_dir <- file.path(sessions_dir,sesh,"images/functional/movement")
  sesh_bolds <- get_boldn_names(sesh=sesh,sessions_dir=sessions_dir) %>% as.data.frame %>% filter(bold_name == bold_name_use)
  if(nrow(sesh_bolds) > 0){
    boldns_use <- sesh_bolds$bold_n %>% as.vector
    for(i in 1:length(boldns_use)){
      boldn <- boldns_use[i] %>% as.character
      boldn_path <- file.path(mov_dir,paste(boldn,".scrub",sep=""))
      mov_scrub <- read.table(boldn_path, header=T)
      percent_udvarsme <- (sum(mov_scrub$udvarsme == 1)/length(mov_scrub$udvarsme)*100) %>% as.numeric %>% signif(3)
      percent_use <- (sum(mov_scrub$udvarsme == 0)/length(mov_scrub$udvarsme)*100) %>% as.numeric %>% signif(3)
      df_out <- cbind(sesh,boldn,bold_name_use,percent_udvarsme,percent_use)
      colnames(df_out) <- c("sesh","bold_n","bold_name","percent_udvarsme","percent_use")
      return(df_out)
    }
  }
}

# get trio movement
percent_udvarsme_trio <- lapply(trio_sessions,function(s) get_percent_udvarsme(sesh=s,sessions_dir=trio_dir,bold_name_use="resting")) %>% do.call(rbind,.) %>% as.data.frame
# get prisma movement
percent_udvarsme_prisma <- lapply(prisma_sessions,function(s) get_percent_udvarsme(sesh=s,sessions_dir=prisma_dir,bold_name_use="restingAP")) %>% do.call(rbind,.) %>% as.data.frame
# get rome movement
percent_udvarsme_rome <- lapply(rome_sessions,function(s) get_percent_udvarsme(sesh=s,sessions_dir=rome_dir,bold_name_use="resting")) %>% do.call(rbind,.) %>% as.data.frame
# get suny movement
percent_udvarsme_suny <- lapply(suny_sessions,function(s) get_percent_udvarsme(sesh=s,sessions_dir=suny_dir,bold_name_use="resting")) %>% do.call(rbind,.) %>% as.data.frame
# get iop movement
percent_udvarsme_iop <- lapply(iop_sessions,function(s) get_percent_udvarsme(sesh=s,sessions_dir=iop_dir,bold_name_use="resting")) %>% do.call(rbind,.) %>% as.data.frame
# get NAPLS movement
percent_udvarsme_napls <- lapply(napls_sessions,function(s) get_percent_udvarsme(sesh=s,sessions_dir=napls_dir,bold_name_use="RESTING")) %>% do.call(rbind,.) %>% as.data.frame

# combine
percent_udvarsme_all <- rbind(percent_udvarsme_trio,percent_udvarsme_prisma,percent_udvarsme_rome,percent_udvarsme_suny,percent_udvarsme_iop, percent_udvarsme_napls)
percent_udvarsme_all$percent_udvarsme <- as.numeric(percent_udvarsme_all$percent_udvarsme)
percent_udvarsme_all$percent_use <- as.numeric(percent_udvarsme_all$percent_use)
percent_udvarsme_all$MRI_S_ID <- percent_udvarsme_all$sesh

# add movement to demo bl
demo_multisite_bl <- merge(x=demo_multisite_bl, y=percent_udvarsme_all[,c("MRI_S_ID","percent_udvarsme")], by="MRI_S_ID", all.x=TRUE)
demo_22q_napls <- merge(x=demo_22q_napls, y=percent_udvarsme_all[,c("MRI_S_ID","percent_udvarsme")], by="MRI_S_ID", all.x=TRUE)
```

demo table
```{r demoTable}
demo_22q_napls_all <- demo_22q_napls

demo_multisite_bl$Group <- factor(demo_multisite_bl$SUBJECT_IDENTITY,levels=c("PATIENT-DEL","CONTROL"),labels=c("22qDel","CONTROL"))
demo_multisite_bl$SEX <- factor(demo_multisite_bl$SEX, levels=c("M","F"))
demo_multisite_bl$cardiac <- factor(demo_multisite_bl$cardiac, levels=c("N","Y"))

#demo_22q_all <- filter(demo_22q_napls_all, Group %in% c("22qDel", "CONTROL")) %>% droplevels
demo_napls_all <- filter(demo_22q_napls_all, Group %in% c("CHR", "CONTROL-N")) %>% droplevels
demo_napls_all$conversion <- "N"
demo_napls_all[which(demo_napls_all$MRI_S_ID %in% convert_ids$MRI_S_ID), "conversion"] <- "Y"
demo_napls_all$conversion %<>% as.factor

# napls IQ
napls_neuro <- read_xlsx(file.path(project,"demographics/NAPLS_Neuro_30Jan2018.xlsx"),trim_ws=T, na=c("","NA"), col_names=T)
napls_neuro1 <- napls_neuro[,c("SiteNumber", "SubjectNumber","VisitLabel","wasiiq")] %>% rename("IQ_full"="wasiiq")
napls_neuro_id <- merge(x=napls_neuro1, y=napls_id_match, by=c("SiteNumber","SubjectNumber"))
demo_napls_all <- merge(x=demo_napls_all, y=napls_neuro_id, by="MRI_S_ID")

# napls meds
napls_meds <- read_xlsx(file.path(project,"demographics/NAPLS2MedsExtraction060616SOPSdatesV1toV7FINALSUMMARY.xlsx"),trim_ws=T, na=c("","NA","#NULL!"), col_names=T)
napls_meds_use <- napls_meds[,c("SiteNumber","SubjectNumber","Index1_current_AP")]
napls_meds_use$Med_Antipsychotic <- factor(napls_meds_use$Index1_current_AP, levels=c(0,1,99), labels=c("N","Y","N"))
demo_napls_all <- merge(x=demo_napls_all, y=napls_meds_use, by=c("SiteNumber","SubjectNumber"))

demo_table_22q <- CreateTableOne(data=demo_multisite_bl, strata="Group", vars=c("AGE","SEX","percent_udvarsme","Med_Antipsychotic","psych_dx", "IQ_full", "cardiac"))
demo_table_22q

demo_table_napls <- CreateTableOne(data=demo_napls_all, strata="Group", vars=c("AGE","SEX","percent_udvarsme","Med_Antipsychotic","conversion","IQ_full"))
demo_table_napls

# print tables
demo_table_22q_f <- print(demo_table_22q, showAllLevels = F, test=T,quote=F, contDigits=1)
demo_table_n_f <- print(demo_table_napls, showAllLevels = F, test=T,quote=F, contDigits=1)
demo_table_n_f <- rbind(demo_table_n_f,"-")
demo_table_all <- cbind(demo_table_22q_f[,c("22qDel","CONTROL","p")],demo_table_n_f[,c("CHR","CONTROL-N","p")])
colnames(demo_table_all) <- c("22qDel","Control22q","p-val-22q","CHR","ControlCHR","p-val-CHR")
rownames(demo_table_all) <- c("n",
                              "Age, Years, Mean (SD)",
                              "Sex, Female, n (%)",
                              "fMRI movement, Mean (SD)",
                              "Antipsychotic med, n (%)",
                              "Psychosis diagnosis, n (%)",
                              "Full Scale IQ, Mean (SD)",
                              "Congenital cardiac diagnosis, n (%)")
demo_table_all %<>% as.data.frame

# use gt() to make table for export
# instructions for bolding specific headers https://gt.rstudio.com/reference/tab_style.html
demo_table_out <- demo_table_all %>% gt(rownames_to_stub=TRUE) %>% 
  tab_style(style = cell_text(weight = "bold"),locations = list(cells_stub(), cells_column_labels())) %>%
  cols_align(align="right", columns=everything())

if(save_outputs==TRUE){
  gtsave(demo_table_out, filename = file.path(project,"figures/demographics/table1.png"))
  gtsave(demo_table_out, filename = file.path(project,"figures/demographics/table1.docx"))
}
```

load fMRI data
```{r loadFMRI}
# read CSV results
# function to read parcellated results and add columns for roi pair name, site, and ID 
read_csv_results <- function(sdir, fname, sesh, site){
  input <- read.csv(file.path(sdir,sesh,"images/functional",fname))
  session <- rep(sesh, times=nrow(input)) %>% as.data.frame
  site <- rep(site, times=nrow(input)) %>% as.data.frame
  new_cols <- cbind(session,site)
  colnames(new_cols) <- c("MRI_S_ID","site")
  output <- cbind(input,new_cols)
  return(output)
}

## file name to look for
# RSFA
rsfa_name <- "resting_parcellated_voxel_RSFA_Atlas_s_hpss_res-mVWM1d_lpss_whole_brain_CABNP.csv"
rsfa_name_prisma <- "restingAP_parcellated_voxel_RSFA_Atlas_s_hpss_res-mVWM1d_lpss_whole_brain_CABNP.csv"
rsfa_name_napls <- "RESTING_parcellated_voxel_RSFA_Atlas_s_hpss_res-mVWM1d_lpss_whole_brain_CABNP.csv"

# local connectivity
netho_name <- "resting_ParcelNetHo_Atlas_s_hpss_res-mVWM1d_lpss_whole_brain_CABNP.csv"
netho_name_prisma <- "restingAP_ParcelNetHo_Atlas_s_hpss_res-mVWM1d_lpss_whole_brain_CABNP.csv"
netho_name_napls <- "RESTING_ParcelNetHo_Atlas_s_hpss_res-mVWM1d_lpss_whole_brain_CABNP.csv"

# between parcel connectivity
bparc_name <- "resting_fc_matrix_Atlas_s_hpss_res-mVWM1d_lpss_CABNP_between_parcel.csv"
bparc_name_prisma <- "restingAP_fc_matrix_Atlas_s_hpss_res-mVWM1d_lpss_CABNP_between_parcel.csv"
bparc_name_napls <- "RESTING_fc_matrix_Atlas_s_hpss_res-mVWM1d_lpss_CABNP_between_parcel.csv"

# read rsfa
trio_rsfa <- lapply(filter(demo_multisite_bl, Site=="UCLAtrio")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="UCLAtrio",sdir=trio_dir,fname=rsfa_name)) %>% do.call(rbind,.)
prisma_rsfa <- lapply(filter(demo_multisite_bl, Site=="UCLAprisma")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="UCLAprisma",sdir=prisma_dir,fname=rsfa_name_prisma)) %>% do.call(rbind,.)
suny_rsfa <- lapply(filter(demo_multisite_bl, Site=="SUNY")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="SUNY",sdir=suny_dir,fname=rsfa_name)) %>% do.call(rbind,.)
rome_rsfa <- lapply(filter(demo_multisite_bl, Site=="Rome")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="Rome",sdir=rome_dir,fname=rsfa_name)) %>% do.call(rbind,.)
iop_rsfa <- lapply(filter(demo_multisite_bl, Site=="IoP")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="IoP",sdir=iop_dir,fname=rsfa_name)) %>% do.call(rbind,.)
napls_rsfa <- lapply(napls_sessions, function(s) read_csv_results(sesh=s,site="NAPLS2",sdir=napls_dir,fname=rsfa_name_napls)) %>% do.call(rbind,.)

rsfa_all <- rbind(trio_rsfa,prisma_rsfa,suny_rsfa,rome_rsfa,iop_rsfa,napls_rsfa)
rsfa_all$INDEX %<>% as.numeric
rsfa_all$t_sd %<>% as.numeric
rsfa_all$t_mean %<>% as.numeric

# read local connectivity
trio_netho <- lapply(filter(demo_multisite_bl, Site=="UCLAtrio")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="UCLAtrio",sdir=trio_dir,fname=netho_name)) %>% do.call(rbind,.)
prisma_netho <- lapply(filter(demo_multisite_bl, Site=="UCLAprisma")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="UCLAprisma",sdir=prisma_dir,fname=netho_name_prisma)) %>% do.call(rbind,.)
suny_netho <- lapply(filter(demo_multisite_bl, Site=="SUNY")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="SUNY",sdir=suny_dir,fname=netho_name)) %>% do.call(rbind,.)
rome_netho <- lapply(filter(demo_multisite_bl, Site=="Rome")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="Rome",sdir=rome_dir,fname=netho_name)) %>% do.call(rbind,.)
iop_netho <- lapply(filter(demo_multisite_bl, Site=="IoP")$MRI_S_ID, function(s) read_csv_results(sesh=s,site="IoP",sdir=iop_dir,fname=netho_name)) %>% do.call(rbind,.)
napls_netho <- lapply(napls_sessions, function(s) read_csv_results(sesh=s,site="NAPLS2",sdir=napls_dir,fname=netho_name_napls)) %>% do.call(rbind,.)

netho_all <- rbind(trio_netho,prisma_netho,suny_netho,rome_netho,iop_netho,napls_netho)
netho_all$INDEX %<>% as.numeric
netho_all$NetHo %<>% as.numeric

# function to convert parcellated fc matrix to global fc by getting the average connectivity for each ROI
gbc_from_matrix <- function(mat, col1="roi_1", col2="roi_2", variable="pearson_r_Fz", rois=1:360, key=ji_key){
  # deprecated line below getting unique rois in favor of choosing rois in function input for more flexibility, with default rois 1:360 (e.g. cortex)
  #rois <- unique(c(mat[,col1],mat[,col2]))
  # make df to filter (rename chosen columns to "col1" and "col2" to easily reference in filter command)
  dat <- mat
  dat$col1 <- dat[,col1]
  dat$col2 <- dat[,col2]
  dat[,variable] %<>% as.numeric
  # filter for only specified rois (default only cortex)
  dat_use <- filter(dat, col1 %in% rois & col2 %in% rois)[,c("MRI_S_ID","site","col1","col2",variable)]
  # get subject ID and site
  id <- unique(dat_use$MRI_S_ID)
  site <- unique(dat_use$site)
  if(length(id)>1){
    stop("Error: more than one MRI ID in input data")
  }
  # make output df with one row per roi
  out <- data.frame(INDEX=rois)
  # get mean fc for each roi
  for(r in rois){
    rows <- filter(dat_use, col1==r | col2==r)
    gbc <- mean(rows[,variable]) 
    out[which(out$INDEX==r),"GBC"] <- gbc
  }
  out <- merge(x=out, y=key, by="INDEX", all.y=TRUE)
  out$MRI_S_ID <- id
  out$site <- site
  return(out)
}

# read between parcel fc CORTEX
trio_gbc <- lapply(filter(demo_multisite_bl, Site=="UCLAtrio")$MRI_S_ID, function(s) gbc_from_matrix(mat=read_csv_results(sesh=s,site="UCLAtrio",sdir=trio_dir,fname=bparc_name))) %>% do.call(rbind,.)

prisma_gbc <- lapply(filter(demo_multisite_bl, Site=="UCLAprisma")$MRI_S_ID, function(s) gbc_from_matrix(mat=read_csv_results(sesh=s,site="UCLAprisma",sdir=prisma_dir,fname=bparc_name_prisma))) %>% do.call(rbind,.)

suny_gbc <- lapply(filter(demo_multisite_bl, Site=="SUNY")$MRI_S_ID, function(s) gbc_from_matrix(mat=read_csv_results(sesh=s,site="SUNY",sdir=suny_dir,fname=bparc_name))) %>% do.call(rbind,.)

rome_gbc <- lapply(filter(demo_multisite_bl, Site=="Rome")$MRI_S_ID, function(s) gbc_from_matrix(mat=read_csv_results(sesh=s,site="Rome",sdir=rome_dir,fname=bparc_name))) %>% do.call(rbind,.)

iop_gbc <- lapply(filter(demo_multisite_bl, Site=="IoP")$MRI_S_ID, function(s) gbc_from_matrix(mat=read_csv_results(sesh=s,site="IoP",sdir=iop_dir,fname=bparc_name))) %>% do.call(rbind,.)

napls_gbc <- lapply(napls_sessions, function(s) gbc_from_matrix(mat=read_csv_results(sesh=s,site="NAPLS2",sdir=napls_dir,fname=bparc_name_napls))) %>% do.call(rbind,.)

gbc_all <- rbind(trio_gbc,prisma_gbc,suny_gbc,rome_gbc,iop_gbc,napls_gbc)
gbc_all$INDEX %<>% as.numeric
gbc_all$GBC %<>% as.numeric
```

Notes on NAPLS QC: 
multiple things to fix in input data
NetHo data initially had NAs as well as inf values
- NA in all "Frontoparietal-29_R-Cerebellum" and "Visual1-04_R-Accumbens" --> check size?
- several subjects have multiple NA (those excluded for short BOLDs marked with *):
  - 02_S0077_00 (700) *
  - 08_S0081_00 (362) *
  - 01_S0074_00 (166) *
  - 08_S0057_00 (11) *
  - 02_S0013_00 (5) - structural QC looks OK
  - 03_S0122_00 (5) - structural QC missing regions including parts of temporal lobe
- several subjects have infinite NetHo values for multiple parcels, and all overlap with cases with multiple NAs
  - 01_S0074_00 (157) *
  - 02_S0077_00 (11) *
  - 08_S0057_00 (141) *
  - 08_S0081_00 (130) *
02_S0077_00 GBC is NA for all parcels *

get info about netho NA parcels
```{r nethoInfo}
# ged indices
r1 <- filter(ji_key, LABEL=="Frontoparietal-29_R-Cerebellum")$INDEX
r2 <- filter(ji_key, LABEL=="Visual1-04_R-Accumbens")$INDEX
#
which(xii_Ji_parcel$data$subcort==r1)
which(xii_Ji_parcel$data$subcort==r2)
# both ROIs assigned NA in NetHo analysis have one single voxel and thus can not calculate NetHo
# need to remove NA rows without disrupting 

# filter NAs from NetHo
netho_no_na <- filter(netho_all, !is.na(NetHo))
```
  
save workspace with initial data
```{r saveInit, paged.print=FALSE}
# save list of packages
setwd(project)
sink("package_versions.txt")
sessionInfo()
sink()

# save image
if(save_outputs==TRUE){
  save.image(file=file.path(project,"demographics/22q_chr_fmri_init.Rdata"),compress = "bzip2")
}
```

harmonize sites with neurocombat
need to harmonize separately for each measure (rsfa, local connectivity, global connectivity)
```{r neuroComBat, message=FALSE, warning=FALSE, paged.print=FALSE}
# function to run neurocombat (includes study defaults)
run_neurocombat <- function(input, 
                            var_column, 
                            site_column="Site",
                            formula="INDEX ~ MRI_S_ID",
                            covars=c("Group","AGE","AGE2","SEX","percent_udvarsme"),
                            model="~Group + AGE + AGE2 + SEX + percent_udvarsme",
                            #covars=c("AGE","AGE2","SEX","percent_udvarsme"),
                            #model="~AGE + AGE2 + SEX + percent_udvarsme",
                            index_col="INDEX", 
                            id_col="MRI_S_ID", 
                            demo=demo_22q_napls){
  # remove site column from input and replace with demo
  input <- subset(input, select=-site)
  input <- merge(x=input, y=demo[,c("MRI_S_ID","Site")], by="MRI_S_ID", all.x=TRUE)
  # get list of indices
  indices <- unique(input$INDEX)
  # cast to wide so that rows are parcel indices and columns are MRI_S_IDs
  data.table::setDT(input)
  input_subcols <- reshape2::dcast(data=input, formula=formula, value.var=var_column) 
  # get subject ids in order of columns
  subcols <- which(names(input_subcols)!= index_col)
  subnames <- names(input_subcols)[subcols]

  # get covariates from multisite baseline demo df, ordered the same as subject ID columns for input to neurocombat
  covardf <- merge(x=data.frame(subnames), y=demo[,c(covars,site_column,id_col)], by.x="subnames", by.y=id_col, all.x=TRUE)
  # drop unused groups to avoid unnecessary factors in model
  covardf$Group %<>% droplevels()
  
  # run neurocombat for parcellated RSFA with site as batch variable and AGE and SEX included in the model
  # using default parametric model (this paper shows parametric prior estimates outperform non-parametric in neurocombat: https://www.sciencedirect.com/science/article/pii/S2666956022000605)
  #model_matrix <- model.matrix(~covardf$AGE + covardf$AGE2 + covardf$SEX + covardf$percent_udvarsme)
  model_matrix <- model.matrix(formula(model),data=covardf[covars])
  #print(summary(as.factor(covardf[,site_column])))
  combat <- neuroCombat(dat=input_subcols[,subcols], batch=covardf[,site_column], mod=model_matrix, parametric=TRUE, eb=TRUE, verbose=FALSE)
  
  # convert combat results  back to long df
  combat_d <- combat$dat.combat %>% as.data.frame
  data.table::setDT(combat_d)
  combat_d$INDEX <- indices
  combat_d$INDEX %<>% as.numeric
  combat_l <- melt.data.table(combat_d, id.vars="INDEX") %>% rename("MRI_S_ID"="variable")
  # merge with input data
  out <- merge(x=input, y=combat_l, by=c("INDEX", "MRI_S_ID"), all.x=TRUE, all.y=TRUE)
  return(out)
}

# use only cortical regions
rsfa_ctx <- filter(rsfa_all, INDEX %in% 1:360)
netho_ctx <- filter(netho_no_na, INDEX %in% 1:360)
gbc_ctx <- filter(gbc_all, INDEX %in% 1:360)

# run combat
rsfa_combat_22q <- run_neurocombat(input=filter(rsfa_ctx, site %in% c("UCLAtrio","UCLAprisma","SUNY","Rome","IoP" )), var_column="t_sd")
rsfa_combat_napls <- run_neurocombat(input=filter(rsfa_ctx, site=="NAPLS2"), var_column="t_sd")
#rsfa_combat <- rbind(rsfa_combat_22q,rsfa_combat_napls)

netho_combat_22q <- run_neurocombat(input=filter(netho_ctx, site %in% c("UCLAtrio","UCLAprisma","SUNY","Rome","IoP" )), var_column="NetHo")
netho_combat_napls <- run_neurocombat(input=filter(netho_ctx, site=="NAPLS2"), var_column="NetHo")
#netho_combat <- rbind(netho_combat_22q,netho_combat_napls)

gbc_combat_22q <- run_neurocombat(input=filter(gbc_ctx, site %in% c("UCLAtrio","UCLAprisma","SUNY","Rome","IoP" )), var_column="GBC")
gbc_combat_napls <- run_neurocombat(input=filter(gbc_ctx, site=="NAPLS2"), var_column="GBC")
#gbc_combat <- rbind(gbc_combat_22q,gbc_combat_napls)

#netho_combat <- run_neurocombat(input=netho_no_na, var_column="NetHo")
#gbc_combat <- run_neurocombat(input=gbc_all, var_column="GBC")

```

normalize based on control group
```{r normalize, message=FALSE, warning=FALSE, paged.print=FALSE}
# function to get mean and standard dev of hcs for a given parcel to use for normalization
# takes as input, a long data frame e.g. gbc_combat, vectors of control IDs, and the desired parcel index 
get_hc_stats <- function(df, hcs_ids, parc){
  dfh <- filter(df, MRI_S_ID %in% hcs_ids & INDEX == parc)
  m <- mean(as.numeric(dfh$value))
  s <- sd(as.numeric(dfh$value))
  out <- data.frame(parcel_hc_mean=m, parcel_hc_sd=s)
  return(out)
}

# function to normalize based on hc mean and sd
hc_normalize <- function(df, hcs_ids){
  # first get hc stats for all parcels
  inds <- unique(df$INDEX)
  hc_stats <- lapply(inds, function(p) get_hc_stats(parc=p, df=df, hcs_ids=hcs_ids)) %>% do.call(rbind,.)
  hc_stats$INDEX <- inds
  # then merge parcel norms with full df
  dfn <- merge(x=df, y=hc_stats, by="INDEX", all.x=TRUE)
  # normalize data in each parcel based on control mean and sd for that parcel
  dfn$value_normed <- (dfn$value - dfn$parcel_hc_mean)/dfn$parcel_hc_sd
  return(dfn)
}

# get list of all controls
hc_ids <- filter(demo_22q_napls, Group=="CONTROL")$MRI_S_ID
hcn_ids <- filter(demo_22q_napls, Group=="CONTROL-N")$MRI_S_ID

# normalize each measure
rsfa_norm_22q <- hc_normalize(df=rsfa_combat_22q, hcs_ids=hc_ids)
rsfa_norm_napls <- hc_normalize(df=rsfa_combat_napls, hcs_ids=hcn_ids)
rsfa_norm <- rbind(rsfa_norm_22q, rsfa_norm_napls)

netho_norm_22q <- hc_normalize(df=netho_combat_22q, hcs_ids=hc_ids)
netho_norm_napls <- hc_normalize(df=netho_combat_napls, hcs_ids=hcn_ids)
netho_norm <- rbind(netho_norm_22q,netho_norm_napls)

gbc_norm_22q <- hc_normalize(df=gbc_combat_22q, hcs_ids=hc_ids)
gbc_norm_napls <- hc_normalize(df=gbc_combat_napls, hcs_ids=hcn_ids)
gbc_norm <- rbind(gbc_norm_22q,gbc_norm_napls)

```

plot pre/post combat
```{r plotComBat}
# function to plot pre and post combat
plot_combat <- function(df, raw_col, title=""){
  # get mean of all parcels per subject pre/post combat to look at distributions
  subs <- sort(unique(df$MRI_S_ID))
  sublist <- lapply(subs, function(s) data.frame(filter(df, MRI_S_ID==s)))
  precombat <- lapply(sublist, function(s) mean(s[,raw_col])) %>% do.call(rbind,.)
  postcombat <- lapply(sublist, function(s) mean(s$value)) %>% do.call(rbind,.)
  parc_means <- data.frame(MRI_S_ID=subs, postcombat=as.vector(postcombat), precombat=as.vector(precombat))
  # add site
  df$duplicated <- duplicated(df$MRI_S_ID)
  dup <- filter(df, duplicated==FALSE)[,c("MRI_S_ID","Site")]
  parc_means_demo <- merge(x=parc_means, y=dup, by="MRI_S_ID")
  parc_means_demo$Site %<>% as.factor
  print(nrow(parc_means))
  print(nrow(parc_means_demo))
  # plot meean RSFA distributions by site pre combat
  pl_precombat <- ggplot(parc_means_demo, aes(precombat, fill=Site, after_stat(count)))+
    geom_density(kernel="gaussian", alpha=0.5)+
    scale_fill_manual(values=rainbow(13))+
    theme_classic()+
    ggtitle(paste("pre-combat",title))
  
  # plot meean RSFA distributions by site post combat
  pl_postcombat <- ggplot(parc_means_demo, aes(postcombat, fill=Site, after_stat(count)))+
    geom_density(kernel="gaussian", alpha=0.5)+ 
    scale_fill_manual(values=rainbow(13))+
    theme_classic()+
    ggtitle(paste("post-combat",title))
  
  ggarrange(pl_precombat,pl_postcombat, nrow=1, common.legend=T,legend="right")
}

plot_normed <- function(df, name){
  # get mean of all parcels per subject pre/post combat to look at distributions
  subs <- sort(unique(df$MRI_S_ID))
  sublist <- lapply(subs, function(s) data.frame(filter(df, MRI_S_ID==s)))
  values <- lapply(sublist, function(s) mean(s$value_normed)) %>% do.call(rbind,.)
  normed <- data.frame(MRI_S_ID=subs, normed=as.vector(values))
  # add site
  df$duplicated <- duplicated(df$MRI_S_ID)
  dup <- filter(df, duplicated==FALSE)[,c("MRI_S_ID","Site")]
  normed_demo <- merge(x=normed, y=dup, by="MRI_S_ID")
  normed_demo$Site %<>% as.factor
  print(nrow(normed_demo))
  print(nrow(normed_demo))
  # plot meean RSFA distributions by site post combat
  pl_postcombat <- ggplot(normed_demo, aes(normed, fill=Site, after_stat(count)))+
  geom_density(kernel="gaussian", alpha=0.5)+ 
  #scale_fill_manual(values=rainbow(13))+
  theme_classic()+
  ggtitle(paste(name,"normed"))
  return(pl_postcombat)
}

norm_plot_rsfa <- plot_normed(rsfa_norm, name="rsfa")
norm_plot_netho <- plot_normed(netho_norm, name="NetHo")
norm_plot_gbc <- plot_normed(gbc_norm, name="gbc")

combat_plot_rsfa <- plot_combat(df=rsfa_norm, raw_col="t_sd", title="RSFA")
combat_plot_netho <- plot_combat(df=netho_norm, raw_col="NetHo", title="NetHo")
combat_plot_gbc <- plot_combat(df=gbc_norm, raw_col="GBC", title="GBC")

norm_plot_rsfa
norm_plot_netho
norm_plot_gbc

combat_plot_rsfa
combat_plot_netho
combat_plot_gbc
```

convert normed combat results back to wide df merged with demographics
```{r demoComBat}
# function to convert long to wide df with indices (renamed to r_index) as columns
rows_to_cols <- function(results, demo, index_colname="INDEX", value_var="value_normed"){
  df <- as.data.frame(results)
  # add prefix "r_" to parcel indices to use as column names in wide df 
  df$index_col <- paste0("r_",df[,index_colname])
  # cast to wide to merge with demographics
  dt <- data.table::setDT(df)
  # list of new column names
  parc_cols <- unique(dt$index_col)
  # make wide df with column from MRI_S_ID and one column per parcel with cells containing normed combat value
  dt_wide <- reshape2::dcast(dt, MRI_S_ID ~ index_col, value.var=value_var) 
  # order cols
  dt_wide_order <- dt_wide[,c("MRI_S_ID", parc_cols)]
  # merge with demo table 
  dt_demo <- merge(x=demo, y=dt_wide_order, by="MRI_S_ID") 
  # return both the data frame and list of results columns
  out <- list(parcels=as.vector(parc_cols), df=as.data.frame(dt_demo))
  return(out)
}

# get list objects with vector of results column names and demo df merged to results
rsfa_wide <- rows_to_cols(results=rsfa_norm, demo=demo_22q_napls)
netho_wide <- rows_to_cols(results=netho_norm, demo=demo_22q_napls)
gbc_wide <- rows_to_cols(results=gbc_norm, demo=demo_22q_napls)
```

test linear models for 22q vs TD and CHR vs TD separately
```{r mainLM, message=FALSE, warning=FALSE, paged.print=FALSE}
# function to return beta coefficient for group in a lm predicting MRI from chosen predictors
lm_parcel_group_covars <- function(df, var, predictors, groups, groupcol, refgroup, test_out_model=FALSE){
  # create formula with var on left side and predictors string on right
  form <- reformulate(predictors,response=var)
  # test linear model
  lm <- lm(formula=form,data=df, na.action="na.omit")
  slm <- summary(lm)
  # get stats for main effect of group
  g <- groups[which(groups != refgroup)]
  gname <- paste0(groupcol,g)
  g_stats <- slm$coefficients[gname,] %>% t %>% as.data.frame
  colnames(g_stats) <- c("group_beta","group_se","group_t","group_p")
  # get stats for site effects
  srows <- grep("Site*", rownames(slm$coefficients))
  s_stats <- slm$coefficients[srows,]
  colnames(s_stats) <- c("beta","se","t","p")
  # convert rows to columns
  s_out <- data.frame()
  for(r in 1:nrow(s_stats)){
    rname <- rownames(s_stats)[r]
    cnames <- paste0(rname,"_",colnames(s_stats))
    s_out[1,cnames] <- s_stats[r,] 
  }
  # option to return full model instead of table for testing purposes
  if(test_out_model==TRUE){
    out <- lm
  }else{
    # add outputs together
    out <- cbind(g_stats,s_out)
  }
  return(out)
}
#test <- lm_parcel_group_covars(df=filter(rsfa_wide$df, Group %in% c("22qDel","CONTROL")), var="r_1",predictors="Group + AGE + AGE2 + SEX + Site + percent_udvarsme",groupcol="Group", groups=c("22qDel","CONTROL"), refgroup="22qDel") 

# function to apply lm at each parcel, expects list object output from rows_to_cols
# defaults, including formula predictors, are set in function but different values can be specified
# groups should be a vector specifying which groups should be ussed
get_parcel_group_lm <- function(list, 
                                groups, 
                                groupcol="Group", 
                                refgroup="CONTROL",
                                sitecol="Site",
                                refsite,
                                covars="AGE + AGE2 + SEX + Site + percent_udvarsme", 
                                alpha=0.05, 
                                roi_key=ji_key,
                                prefix="r_",
                                filter=FALSE,
                                filtercol="",
                                filterin=""){
  if(length(groups)!=2){ stop("Error: number of groups not equal to 2")}
  # add group to string of model variables
  predictors <- paste(groupcol, "+", covars)
  # filter by specified groups and relevel factor
  df_all <- as.data.frame(list$df)
  df_all$groupcol <- df_all[,groupcol]
  # filter data based to keep only rows wither value of filtercol is in filterin
  if(filter==TRUE){
    dff <- df_all %>% filter(.data[[filtercol]] %in% filterin)
  }else{
    dff <- df_all
  }
  # filter groupcol in groups
  df <- filter(dff, groupcol %in% groups)
  df[,groupcol] <- relevel(as.factor(df[,groupcol]), ref=refgroup)
  # relevel site
  df[,sitecol] <- relevel(as.factor(df[,sitecol]), ref=refsite)
  # do linear model for every parcel, FDR correct p-values, and create column of betas set to NA when not FDR significant
  parc_cols <- list$parcels
  stats <- lapply(parc_cols, function(v) lm_parcel_group_covars(var=v, df=df, predictors=predictors, groups=groups, groupcol=groupcol, refgroup=refgroup)) %>% do.call(rbind,.) %>% as.data.frame
  #colnames(stats) <- c("group_beta","group_se","group_t","group_p")
  stats$group_FDR_q <- p.adjust(stats$group_p, method="fdr")
  stats$group_FDR_sig <- stats$group_FDR_q < alpha
  stats$group_beta_FDR <- stats$group_beta
  stats$group_beta_FDR[which(stats$group_FDR_sig != TRUE)] <- NA
  # add index column and merge with roi key (assumes column named INDEX in roi_key)
  stats$indexcol <- parc_cols
  stats$INDEX <- gsub(prefix,"",stats$indexcol)
  out <- merge(x=roi_key, y=stats, by="INDEX", all.x=TRUE, all.y=TRUE)
  return(out)
}
#test <- get_parcel_group_lm(list=rsfa_wide, groups=c("22qDel","CONTROL"),refgroup="CONTROL", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360))

# get main effects of group for each measure
rsfa_22q_lms <- get_parcel_group_lm(list=rsfa_wide, groups=c("22qDel","CONTROL"), refgroup="CONTROL", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("RSFA 22q significant regions:",sum(rsfa_22q_lms$group_FDR_sig)))

rsfa_chr_lms <- get_parcel_group_lm(list=rsfa_wide, groups=c("CHR","CONTROL-N"), refgroup="CONTROL-N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("RSFA CHR significant regions:",sum(rsfa_chr_lms$group_FDR_sig)))

netho_22q_lms <- get_parcel_group_lm(list=netho_wide, groups=c("22qDel","CONTROL"), refgroup="CONTROL", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("NetHo 22q significant regions:",sum(netho_22q_lms$group_FDR_sig, na.rm=TRUE)))

netho_chr_lms <- get_parcel_group_lm(list=netho_wide, groups=c("CHR","CONTROL-N"), refgroup="CONTROL-N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("NetHo CHR significant regions:",sum(netho_chr_lms$group_FDR_sig, na.rm=TRUE)))

gbc_22q_lms <- get_parcel_group_lm(list=gbc_wide, groups=c("22qDel","CONTROL"), refgroup="CONTROL", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("GBC 22q significant regions:",sum(gbc_22q_lms$group_FDR_sig)))

gbc_chr_lms <- get_parcel_group_lm(list=gbc_wide, groups=c("CHR","CONTROL-N"), refgroup="CONTROL-N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("GBC CHR significant regions:",sum(gbc_chr_lms$group_FDR_sig)))
```

test CHRc vs TD and CHRc vs CHR
```{r chrcLM}
# test CHRc vs CONTROL-N
rsfa_chrc_lms <- get_parcel_group_lm(list=rsfa_wide, groups=c("CHRc","CONTROL-N"), groupcol="GroupConvert", refgroup="CONTROL-N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("RSFA CHRc vs Control significant regions:",sum(rsfa_chrc_lms$group_FDR_sig)))

netho_chrc_lms <- get_parcel_group_lm(list=netho_wide, groups=c("CHRc","CONTROL-N"), groupcol="GroupConvert", refgroup="CONTROL-N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("NetHo CHRc vs Control significant regions:",sum(netho_chrc_lms$group_FDR_sig)))

gbc_chrc_lms <- get_parcel_group_lm(list=gbc_wide, groups=c("CHRc","CONTROL-N"), groupcol="GroupConvert", refgroup="CONTROL-N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("GBC CHRc vs Control significant regions:",sum(gbc_chrc_lms$group_FDR_sig)))

# test CHRc vs CHR
rsfa_chrcchr_lms <- get_parcel_group_lm(list=rsfa_wide, groups=c("CHRc","CHR"), groupcol="GroupConvert", refgroup="CHR", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("RSFA CHRc vs CHR significant regions:",sum(rsfa_chrcchr_lms$group_FDR_sig)))

netho_chrcchr_lms <- get_parcel_group_lm(list=netho_wide, groups=c("CHRc","CHR"), groupcol="GroupConvert", refgroup="CHR", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("NetHo CHRc vs CHR significant regions:",sum(netho_chrcchr_lms$group_FDR_sig)))

gbc_chrcchr_lms <- get_parcel_group_lm(list=gbc_wide, groups=c("CHRc","CHR"), groupcol="GroupConvert", refgroup="CHR", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360))
print(paste("GBC CHRc vs CHR significant regions:",sum(gbc_chrcchr_lms$group_FDR_sig)))
```

save workspace with main data
```{r saveMain, paged.print=FALSE}
# save image
if(save_outputs==TRUE){
  save.image(file=file.path(project,"git_exclude/22q_chr_fmri_main.Rdata"),compress = "gzip")
}
```

plot group difference maps
```{r funcPlotMRI, message=FALSE, warning=FALSE, paged.print=FALSE}
# function to take xifti atlas (with ROIs denoted by unique values) and return list of xifti matrix indices by brain structure for each ROI
get_roi_atlas_inds <- function(xii){
  # get all unique roi labels
  mxii <- as.matrix(xii)
  vals <- mxii %>% unique %>% sort %>% as.numeric
  # get brain structures to iterate through (cortex_left, cortex_right, subcort)
  xiinames <- names(xii$data)
  # for each ROI, get the indices for each brain structure
  # output is a nested list for each ROI (with "r_" added as prefix) and each brain structure, containing an array of xifti indices corresponding to the ROI in a given brain structure
  out <- lapply(setNames(vals,paste0("r_",vals)), function(v) lapply(setNames(xiinames,xiinames), function(n) which(xii$data[[n]] == v)))
  return(out)
}

# function to create xifti for plotting ROI values on a brain atlas
# input atlas xifti and data frame with at least two cols corresponding to ROI IDs (roi_col) and output values (val_col) e.g. gene expression or functional connectivity
# output modified atlas xifti with ROI IDs replaced with output values (for visualization)
atlas_xifti_new_vals <- function(xii, df, roi_col, val_col){
  # get list of xifti indices for each ROI
  inds <- get_roi_atlas_inds(xii)
  # create blank xii from atlas
  xii_out <- xii
  for (struct in names(xii_out$data)){
    if (!is.null(xii_out$data[[struct]])){
      xii_out$data[[struct]] <- as.matrix(rep(NA,times=nrow(xii_out$data[[struct]])))
    }
  }
  # create new column named roilabel from roi_col
  df$roilabel <- df[,roi_col]
  # for each roi in xii, set all relevant vertices to value from val_col based on roi_col
  for (roi in names(inds)){
    #print(roi)
    # get value for roi
    out_val <- as.numeric(filter(df[,c("roilabel",val_col)], roilabel==gsub("r_","",roi))[val_col])
    #print(out_val)
    # loop through brain structures, if ROI has any indices in a structure, set those to the output value
    for (struct in names(inds[[roi]])){
      roi_inds <- inds[[roi]][[struct]]
      l <- length(roi_inds)
      if (l > 0){
        xii_out$data[[struct]][roi_inds] <- out_val
      }
    }
  }
  return(xii_out)
}

# color pals for brain plots
# set up rcolorbrewer palettes
pal_red_yellow_blue <- function(){
  pal <- "RdYlBu"
  ncolors <- 1000
  mycolors <- rev(colorRampPalette(brewer.pal(11,pal))(ncolors))
  return(mycolors)
}

pal_red_blue <- function(){
  pal <- "RdBu"
  ncolors <- 1000
  mycolors <- rev(colorRampPalette(brewer.pal(11,pal))(ncolors))
  return(mycolors)
}

pal_yellow_orange_red <- function(){
  pal <- "YlOrRd"
  ncolors <- 1000
  mycolors <- colorRampPalette(brewer.pal(9,pal))(ncolors)
  return(mycolors)
}
```

```{r plotMRI}
# plot group difference beta only fdr<0.05
# 22q RSFA
pl_rsfa_22q_b_fdr <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_lms, roi_col="INDEX", val_col="group_beta_FDR")
view_xifti_surface(pl_rsfa_22q_b_fdr, title="Signal Variablity: 22qDel vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_rsfa_22q_b_fdr,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/rsfa_22q_b_fdr.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# 22q NetHo
pl_netho_22q_b_fdr <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=netho_22q_lms, roi_col="INDEX", val_col="group_beta_FDR")
view_xifti_surface(pl_netho_22q_b_fdr, title="Local Connectivity: 22qDel vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_netho_22q_b_fdr,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/netho_22q_b_fdr.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# 22q GBC
pl_gbc_22q_b_fdr <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=gbc_22q_lms, roi_col="INDEX", val_col="group_beta_FDR")
view_xifti_surface(pl_gbc_22q_b_fdr, title="Global Connectivity: 22qDel vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_gbc_22q_b_fdr,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/gbc_22q_b_fdr.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# plot group difference beta 
# 22q RSFA
pl_rsfa_22q_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_lms, roi_col="INDEX", val_col="group_beta")
view_xifti_surface(pl_rsfa_22q_b, title="Signal Variablity: 22qDel vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_rsfa_22q_b,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/rsfa_22q_b.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# 22q NetHo
pl_netho_22q_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=netho_22q_lms, roi_col="INDEX", val_col="group_beta")
view_xifti_surface(pl_netho_22q_b, title="Local Connectivity: 22qDel vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_netho_22q_b,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/netho_22q_b.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# 22q GBC
pl_gbc_22q_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=gbc_22q_lms, roi_col="INDEX", val_col="group_beta")
view_xifti_surface(pl_gbc_22q_b, title="Global Connectivity: 22qDel vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_gbc_22q_b,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/gbc_22q_b.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}
# plot CHR netho FDR beta
# chr NetHo
pl_netho_chr_b_fdr <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=netho_chr_lms, roi_col="INDEX", val_col="group_beta_FDR")
view_xifti_surface(pl_netho_chr_b_fdr, title="Local Connectivity: CHR vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_netho_chr_b_fdr,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/netho_chr_b_fdr.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# plot CHR threshold free beta
# chr RSFA
pl_rsfa_chr_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_chr_lms, roi_col="INDEX", val_col="group_beta")
view_xifti_surface(pl_rsfa_chr_b, title="Signal Variablity: CHR vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_rsfa_chr_b,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/rsfa_chr_b.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# chr NetHo
pl_netho_chr_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=netho_chr_lms, roi_col="INDEX", val_col="group_beta")
view_xifti_surface(pl_netho_chr_b, title="Local Connectivity: CHR vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_netho_chr_b,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/netho_chr_b.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}

# chr GBC
pl_gbc_chr_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=gbc_chr_lms, roi_col="INDEX", val_col="group_beta")
view_xifti_surface(pl_gbc_chr_b, title="Global Connectivity: CHR vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# save
if(save_outputs==TRUE){
  view_xifti_surface(pl_gbc_chr_b,zlim=c(-0.8,0.8), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/gbc_chr_b.png"),legend_embed=FALSE, legend_fname = file.path(project,"figures/fmri_maps/legend.png"))
}
```

test control means
```{r cMean}
# example df to end up with rsfa_22q_lms

# start with rsfa_combat_22q

# function to get ROI means
get_roi_means <- function(combat_result, group, demo=demo_22q_napls){
  wide <- rows_to_cols(results=combat_result, demo=demo, value_var = "value")
  wide_c <- filter(wide$df, Group==group)
  c_means <- colMeans(wide_c[,wide$parcels])
  df <- data.frame(roi=names(c_means),value=c_means)
  df$INDEX <- gsub("r_","",df$roi) %>% as.numeric
  return(df)
}

# 22q Control 
control_22q_rsfa <- get_roi_means(combat_result=rsfa_combat_22q, group="CONTROL")
control_22q_netho <- get_roi_means(combat_result=netho_combat_22q, group="CONTROL")
control_22q_gbc <- get_roi_means(combat_result=gbc_combat_22q, group="CONTROL")

# NAPLS Control
control_n_rsfa <- get_roi_means(combat_result=rsfa_combat_napls, group="CONTROL-N")
control_n_netho <- get_roi_means(combat_result=netho_combat_napls, group="CONTROL-N")
control_n_gbc <- get_roi_means(combat_result=gbc_combat_napls, group="CONTROL-N")
```

plot control means
```{r plotControl}
save_outputs=TRUE

# BSV
pl_rsfa_control_22q <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=control_22q_rsfa, roi_col="INDEX", val_col="value")
view_xifti_surface(pl_rsfa_control_22q, title="Control22q Mean BSV", cex.title=1.3, colors="viridis")
if(save_outputs==TRUE){
  view_xifti_surface(pl_rsfa_control_22q, colors="viridis", fname=file.path(project,"figures/fmri_maps/control22q_bsv.png"),legend_embed=TRUE, title="Control22q Mean BSV", cex.title=2.5)
}

pl_rsfa_control_n <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=control_n_rsfa, roi_col="INDEX", val_col="value")
view_xifti_surface(pl_rsfa_control_n, title="ControlCHR Mean BSV", cex.title=1.3, colors="viridis")
if(save_outputs==TRUE){
  view_xifti_surface(pl_rsfa_control_n, colors="viridis", fname=file.path(project,"figures/fmri_maps/controlCHR_bsv.png"),legend_embed=TRUE, title="ControlCHR Mean BSV", cex.title=2.5)
}

# LC
pl_netho_control_22q <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=control_22q_netho, roi_col="INDEX", val_col="value")
view_xifti_surface(pl_netho_control_22q, title="Control22q Mean LC", cex.title=1.3, colors="viridis")
if(save_outputs==TRUE){
  view_xifti_surface(pl_netho_control_22q, colors="viridis", fname=file.path(project,"figures/fmri_maps/control22q_lc.png"),legend_embed=TRUE, title="Control22q Mean LC", cex.title=2.5)
}


pl_netho_control_n <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=control_n_netho, roi_col="INDEX", val_col="value")
view_xifti_surface(pl_netho_control_n, title="ControlCHR Mean LC", cex.title=1.3, colors="viridis")
if(save_outputs==TRUE){
  view_xifti_surface(pl_netho_control_n, colors="viridis", fname=file.path(project,"figures/fmri_maps/controlCHR_lc.png"),legend_embed=TRUE, title="ControlCHR Mean LC", cex.title=2.5)
}

# GBC
pl_gbc_control_22q <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=control_22q_gbc, roi_col="INDEX", val_col="value")
view_xifti_surface(pl_gbc_control_22q, title="Control22q Mean GBC", cex.title=1.3, colors="viridis")
if(save_outputs==TRUE){
  view_xifti_surface(pl_gbc_control_22q, colors="viridis", fname=file.path(project,"figures/fmri_maps/control22q_gbc.png"),legend_embed=TRUE, title="Control22q Mean GBC", cex.title=2.5)
}

pl_gbc_control_n <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=control_n_gbc, roi_col="INDEX", val_col="value")
view_xifti_surface(pl_gbc_control_n, title="ControlCHR Mean GBC", cex.title=1.3, colors="viridis")
if(save_outputs==TRUE){
  view_xifti_surface(pl_gbc_control_n, colors="viridis", fname=file.path(project,"figures/fmri_maps/controlCHR_gbc.png"),legend_embed=TRUE, title="ControlCHR Mean GBC", cex.title=2.5)
}

save_outputs=FALSE

# print standard deviations for control maps
print(paste("Control22q GBC SD:",sd(control_22q_gbc$value)))
print(paste("ControlCHR GBC SD:",sd(control_n_gbc$value)))

print(paste("Control22q BSV SD:",sd(control_22q_rsfa$value)))
print(paste("ControlCHR BSV SD:",sd(control_n_rsfa$value)))

print(paste("Control22q LC SD:",sd(control_22q_netho$value)))
print(paste("ControlCHR LC SD:",sd(control_n_netho$value)))
```

write files for brainsmash null model generation
needs separate txt files per hemisphere with values ordered by ascending parcel ID
```{r writeBsmash}
# set to TRUE to save brainsmash outputs
save_bsmash_outputs=FALSE

# RSFA Left cortex
rsfa_22q_lms_L <- filter(rsfa_22q_lms, INDEX <= 180)
rsfa_22q_lms_L_b <- rsfa_22q_lms_L[order(rsfa_22q_lms_L$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(rsfa_22q_lms_L_b, file=file.path(project,"CAB-NP/22q_TD_RSFA_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# RSFA Right cortex
rsfa_22q_lms_R <- filter(rsfa_22q_lms, INDEX > 180 & INDEX <= 360)
rsfa_22q_lms_R_b <- rsfa_22q_lms_R[order(rsfa_22q_lms_R$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(rsfa_22q_lms_R_b, file=file.path(project,"CAB-NP/22q_TD_RSFA_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# NetHo Left cortex
netho_22q_lms_L <- filter(netho_22q_lms, INDEX <= 180)
netho_22q_lms_L_b <- netho_22q_lms_L[order(netho_22q_lms_L$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(netho_22q_lms_L_b, file=file.path(project,"CAB-NP/22q_TD_NetHo_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# NetHo Right cortex
netho_22q_lms_R <- filter(netho_22q_lms, INDEX > 180 & INDEX <= 360)
netho_22q_lms_R_b <- netho_22q_lms_R[order(netho_22q_lms_R$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(netho_22q_lms_R_b, file=file.path(project,"CAB-NP/22q_TD_NetHo_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# gbc Left cortex
gbc_22q_lms_L <- filter(gbc_22q_lms, INDEX <= 180)
gbc_22q_lms_L_b <- gbc_22q_lms_L[order(gbc_22q_lms_L$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(gbc_22q_lms_L_b, file=file.path(project,"CAB-NP/22q_TD_GBC_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# gbc Right cortex
gbc_22q_lms_R <- filter(gbc_22q_lms, INDEX > 180 & INDEX <= 360)
gbc_22q_lms_R_b <- gbc_22q_lms_R[order(gbc_22q_lms_R$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(gbc_22q_lms_R_b, file=file.path(project,"CAB-NP/22q_TD_GBC_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

#####

# RSFA Left cortex CHR
rsfa_chr_lms_L <- filter(rsfa_chr_lms, INDEX <= 180)
rsfa_chr_lms_L_b <- rsfa_chr_lms_L[order(rsfa_chr_lms_L$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(rsfa_chr_lms_L_b, file=file.path(project,"CAB-NP/CHR_TD_RSFA_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# RSFA Right cortex CHR
rsfa_chr_lms_R <- filter(rsfa_chr_lms, INDEX > 180 & INDEX <= 360)
rsfa_chr_lms_R_b <- rsfa_chr_lms_R[order(rsfa_chr_lms_R$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(rsfa_chr_lms_R_b, file=file.path(project,"CAB-NP/CHR_TD_RSFA_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# NetHo Left cortex CHR
netho_chr_lms_L <- filter(netho_chr_lms, INDEX <= 180)
netho_chr_lms_L_b <- netho_chr_lms_L[order(netho_chr_lms_L$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(netho_chr_lms_L_b, file=file.path(project,"CAB-NP/CHR_TD_NetHo_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# NetHo Right cortex CHR
netho_chr_lms_R <- filter(netho_chr_lms, INDEX > 180 & INDEX <= 360)
netho_chr_lms_R_b <- netho_chr_lms_R[order(netho_chr_lms_R$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(netho_chr_lms_R_b, file=file.path(project,"CAB-NP/CHR_TD_NetHo_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# gbc Left cortex CHR
gbc_chr_lms_L <- filter(gbc_chr_lms, INDEX <= 180)
gbc_chr_lms_L_b <- gbc_chr_lms_L[order(gbc_chr_lms_L$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(gbc_chr_lms_L_b, file=file.path(project,"CAB-NP/CHR_TD_GBC_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

# gbc Right cortex CHR
gbc_chr_lms_R <- filter(gbc_chr_lms, INDEX > 180 & INDEX <= 360)
gbc_chr_lms_R_b <- gbc_chr_lms_R[order(gbc_chr_lms_R$INDEX),"beta"]
if(save_bsmash_outputs==TRUE){
  write.table(gbc_chr_lms_R_b, file=file.path(project,"CAB-NP/CHR_TD_GBC_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}

#####
# write control means
# 22q Control 
control_22q_rsfa_L <- filter(control_22q_rsfa, INDEX <= 180)[,"value"]
if(save_bsmash_outputs==TRUE){
  write.table(control_22q_rsfa_L, file=file.path(project,"CAB-NP/control_22q_rsfa_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_22q_netho_L <- filter(control_22q_netho, INDEX <= 180)[,"value"]
if(save_bsmash_outputs==TRUE){
  write.table(control_22q_netho_L, file=file.path(project,"CAB-NP/control_22q_netho_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_22q_gbc_L <- filter(control_22q_gbc, INDEX <= 180)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_22q_gbc_L, file=file.path(project,"CAB-NP/control_22q_gbc_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}


control_22q_rsfa_R <- filter(control_22q_rsfa, INDEX > 180 & INDEX <= 360)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_22q_rsfa_R, file=file.path(project,"CAB-NP/control_22q_rsfa_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_22q_netho_R <- filter(control_22q_netho, INDEX > 180 & INDEX <= 360)[,"value"]
if(save_bsmash_outputs==TRUE){
  write.table(control_22q_netho_R, file=file.path(project,"CAB-NP/control_22q_netho_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_22q_gbc_R <- filter(control_22q_gbc, INDEX > 180 & INDEX <= 360)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_22q_gbc_R, file=file.path(project,"CAB-NP/control_22q_gbc_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}


control_n_rsfa_L <- filter(control_n_rsfa, INDEX <= 180)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_n_rsfa_L, file=file.path(project,"CAB-NP/control_n_rsfa_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_n_netho_L <- filter(control_n_netho, INDEX <= 180)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_n_netho_L, file=file.path(project,"CAB-NP/control_n_netho_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_n_gbc_L <- filter(control_n_gbc, INDEX <= 180)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_n_gbc_L, file=file.path(project,"CAB-NP/control_n_gbc_L.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}


control_n_rsfa_R <- filter(control_n_rsfa, INDEX > 180 & INDEX <= 360)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_n_rsfa_R, file=file.path(project,"CAB-NP/control_n_rsfa_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_n_netho_R <- filter(control_n_netho, INDEX > 180 & INDEX <= 360)[,"value"]
if(save_bsmash_outputs==TRUE){
  write.table(control_n_netho_R, file=file.path(project,"CAB-NP/control_n_netho_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}
control_n_gbc_R <- filter(control_n_gbc, INDEX > 180 & INDEX <= 360)[,"value"] 
if(save_bsmash_outputs==TRUE){
  write.table(control_n_gbc_R, file=file.path(project,"CAB-NP/control_n_gbc_R.txt"), quote=FALSE, col.names = FALSE, row.names = FALSE)
}


```

next step involves creating brainsmash permutations using python script in same repo, then read those results back into R and continue

read brainsmash outputs
```{r readBsmash}
# function to read brainsmash outputs, which are CSVs with one column per parcel and one row per shuffled brain
# needs path to csv, vector of indices (e.g. 1:180 or 181:360), and a key dataframe
# output will be key df merged with n brainsmash columns named V1:Vn, with rows not in indices set to NA
read_brainsmash <- function(path, indices, key=ji_key){
  df <- read.csv(path,header=FALSE)
  # transpose so that rows are indices and columns are replicates
  dft <- as.data.frame(t(df))
  # add index column
  dft$INDEX <- indices
  rownames(dft) <- indices
  # merge with key
  out <- merge(x=dft, all.x=TRUE, y=key, all.y=TRUE, by="INDEX")
  return(out)
}

rsfa_22q_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/22q_TD_RSFA_L_permuted.csv"), indices=1:180)
rsfa_22q_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/22q_TD_RSFA_R_permuted.csv"), indices=181:360)
netho_22q_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/22q_TD_NetHo_L_permuted.csv"), indices=1:180)
netho_22q_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/22q_TD_NetHo_R_permuted.csv"), indices=181:360)
gbc_22q_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/22q_TD_GBC_L_permuted.csv"), indices=1:180)
gbc_22q_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/22q_TD_GBC_R_permuted.csv"), indices=181:360)

rsfa_chr_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/CHR_TD_RSFA_L_permuted.csv"), indices=1:180)
rsfa_chr_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/CHR_TD_RSFA_R_permuted.csv"), indices=181:360)
netho_chr_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/CHR_TD_NetHo_L_permuted.csv"), indices=1:180)
netho_chr_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/CHR_TD_NetHo_R_permuted.csv"), indices=181:360)
gbc_chr_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/CHR_TD_GBC_L_permuted.csv"), indices=1:180)
gbc_chr_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/CHR_TD_GBC_R_permuted.csv"), indices=181:360)


# plot a few shuffled brains
# view_xifti_surface(atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_bsmash_L, roi_col="INDEX", val_col="V1"), title="BrainSMASH, RSFA, L, 1", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# view_xifti_surface(atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_bsmash_L, roi_col="INDEX", val_col="V5"), title="BrainSMASH, RSFA, L, 5", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# view_xifti_surface(atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_bsmash_L, roi_col="INDEX", val_col="V100"), title="BrainSMASH, RSFA, L, 100", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# view_xifti_surface(atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_bsmash_R, roi_col="INDEX", val_col="V1000"), title="BrainSMASH, RSFA, R, 1000", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())
# view_xifti_surface(atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_bsmash_R, roi_col="INDEX", val_col="V10000"), title="BrainSMASH, RSFA, R, 10000", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue())

# read control means
rsfa_control_22q_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/control_22q_rsfa_L_permuted.csv"), indices=1:180)
rsfa_control_22q_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/control_22q_rsfa_R_permuted.csv"), indices=181:360)
netho_control_22q_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/control_22q_netho_L_permuted.csv"), indices=1:180)
netho_control_22q_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/control_22q_netho_R_permuted.csv"), indices=181:360)
gbc_control_22q_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/control_22q_gbc_L_permuted.csv"), indices=1:180)
gbc_control_22q_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/control_22q_gbc_R_permuted.csv"), indices=181:360)

rsfa_control_n_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/control_n_rsfa_L_permuted.csv"), indices=1:180)
rsfa_control_n_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/control_n_rsfa_R_permuted.csv"), indices=181:360)
netho_control_n_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/control_n_netho_L_permuted.csv"), indices=1:180)
netho_control_n_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/control_n_netho_R_permuted.csv"), indices=181:360)
gbc_control_n_bsmash_L <- read_brainsmash(path=file.path(project,"CAB-NP/control_n_gbc_L_permuted.csv"), indices=1:180)
gbc_control_n_bsmash_R <- read_brainsmash(path=file.path(project,"CAB-NP/control_n_gbc_R_permuted.csv"), indices=181:360)
# view_xifti_surface(atlas_xifti_new_vals(xii=xii_Ji_parcel, df=gbc_control_n_bsmash_R, roi_col="INDEX", val_col="V6000"), title="BrainSMASH", cex.title=1.3, colors=pal_red_blue())
```

compare case-control maps via permutation
```{r permCor}
# function to compute correlation between two brain maps and compare to brainsmash null distribution
# requires df for brain map1, and df and brainsmash output for map2
# outputs list object with true correlation and vector for null distribution
perm_cor_brain_map <- function(map1, map2, bsmash2, cols=paste0("V",1:10000), val_col1="group_beta", val_col2="group_beta", method){
  # get list of parcels in brainsmash data (e.g. left hemisphere only)
  indices <- bsmash2[which(!is.na(bsmash2$V1)),"INDEX"]
  # filter input for only those
  fmap1 <- filter(map1, INDEX %in% indices) 
  fmap2 <- filter(map2, INDEX %in% indices)
  # merge data
  m1 <- data.frame(INDEX=fmap1[,"INDEX"], col1=fmap1[,val_col1])
  m2 <- data.frame(INDEX=fmap2[,"INDEX"], col2=fmap2[,val_col2])
  m3 <- merge(x=m1, y=m2, by="INDEX")
  df <- merge(x=bsmash2, y=m3, by="INDEX")
  # true correlation
  cor <- cor(x=as.numeric(m3$col1), y=as.numeric(m3$col2), use="complete.obs", method=method)
  # correlate with shuffled brains
  nulls <- lapply(cols, function(c) cor(x=as.numeric(df$col1), y=as.numeric(df[,c]), use="complete.obs", method=method)) %>% unlist %>% as.vector
  out <- list(true_correlation=cor, nulls=nulls)
}

# function to get permuted two-tailed p-value
perm_p <- function(test_stat, nulls, alternative="two.sided", verbose=FALSE){
  if(alternative=="two.sided"){
    sum <- sum(abs(nulls) > abs(test_stat))
  }else if(alternative=="greater"){
    sum <- sum(nulls > test_stat)
  }else if(alternative=="less"){
    sum <- sum(nulls < test_stat)
  }
  len <- length(nulls)
  out <- sum/len
  if(verbose==TRUE){
    print(sum)
    print(len)
    print(out)
  }
  return(out)
}

# function to plot true correlation vs nulls
plot_cor_nulls <- function(test_stat, nulls, alternative="two.sided",ylab="",title="", xlab="test statistic"){
  p <- perm_p(test_stat=test_stat, nulls=nulls, alternative=alternative)
  ggplot(data=data.frame(nulls=nulls), aes(x=nulls))+
    geom_histogram(bins=40,fill="slategrey", alpha=0.7)+
    geom_vline(xintercept=test_stat, color="red", linewidth=1, lty="solid")+
    #geom_label_repel(data=data.frame(xval=test_stat, text=paste("p =",round(p, digits=7))), aes(x=xval, y=0, label=text), min.segment.length = 0, nudge_y=100, nudge_x=-0.05)+
    geom_label_repel(data=data.frame(xval=test_stat, text=paste("p =",p)), aes(x=xval, y=0, label=text), min.segment.length = 0, nudge_y=100, nudge_x=-0.05)+
    xlab(xlab)+
    ylab(ylab)+
    ggtitle(title)+
    theme_classic()
}
```

```{r plotPermCor}
# make data frame to record correlations between pairs of maps  
#map_cor <- data.frame(map1=c("22q_lc", "22q_bsv", "chr_gbc", "chr_lc", "chr_bsv", "22q_bsv", "chr_gbc", "chr_lc", "chr_bsv", "chr_gbc", "chr_lc", "chr_bsv", "chr_lc", "chr_bsv", "chr_bsv"), map2=c("22q_gbc", "22q_gbc", "22q_gbc", "22q_gbc", "22q_gbc", "22q_lc", "22q_lc", "22q_lc", "22q_lc", "22q_bsv", "22q_bsv", "22q_bsv", "chr_gbc", "chr_gbc", "chr_lc"))  

#maps_all <- c("22q_gbc","22q_lc","22q_bsv","chr_gbc","chr_lc","chr_bsv")  
maps_all <- c("22q GBC","22q LC","22q BSV","CHR LC")  
#maps_all_df <- expand.grid(maps_all,maps_all) %>% filter(., Var1 != Var2)
maps_all_df <- expand.grid(maps_all,maps_all)

# get bilateral correlations
get_bilat_cor <- function(var1, var2){
  if(var1== "22q LC" & var2 == "22q GBC"){
    L <- perm_cor_brain_map(map1=netho_22q_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_22q_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_R, method="pearson")
  }else if(var1== "22q BSV" & var2 == "22q GBC"){
    L <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR GBC" & var2 == "22q GBC"){
    L <- perm_cor_brain_map(map1=gbc_chr_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_chr_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR LC" & var2 == "22q GBC"){
    L <- perm_cor_brain_map(map1=netho_chr_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_chr_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR BSV" & var2 == "22q GBC"){
    L <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=gbc_22q_lms, bsmash2=gbc_22q_bsmash_R, method="pearson")
  }else if(var1== "22q GBC" & var2 == "22q LC"){
    L <- perm_cor_brain_map(map1=gbc_22q_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_22q_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_R, method="pearson")
  }else if(var1== "22q BSV" & var2 == "22q LC"){
    L <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR GBC" & var2 == "22q LC"){
    L <- perm_cor_brain_map(map1=gbc_chr_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_chr_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR LC" & var2 == "22q LC"){
    L <- perm_cor_brain_map(map1=netho_chr_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_chr_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR BSV" & var2 == "22q LC"){
    L <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=netho_22q_lms, bsmash2=netho_22q_bsmash_R, method="pearson")
  }else if(var1== "22q GBC" & var2 == "22q BSV"){
    L <- perm_cor_brain_map(map1=gbc_22q_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_22q_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_R, method="pearson")
  }else if(var1== "22q LC" & var2 == "22q BSV"){
    L <- perm_cor_brain_map(map1=netho_22q_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_22q_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR GBC" & var2 == "22q BSV"){
    L <- perm_cor_brain_map(map1=gbc_chr_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_chr_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR LC" & var2 == "22q BSV"){
    L <- perm_cor_brain_map(map1=netho_chr_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_chr_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_R, method="pearson")
  }else if(var1== "CHR BSV" & var2 == "22q BSV"){
    L <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=rsfa_22q_lms, bsmash2=rsfa_22q_bsmash_R, method="pearson")
  }else if(var1== "22q GBC" & var2 == "CHR GBC"){
    L <- perm_cor_brain_map(map1=gbc_22q_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_22q_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_R, method="pearson")
  }else if(var1== "22q LC" & var2 == "CHR GBC"){
    L <- perm_cor_brain_map(map1=netho_22q_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_22q_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_R, method="pearson")
  }else if(var1== "22q BSV" & var2 == "CHR GBC"){
    L <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_R, method="pearson")
  }else if(var1== "CHR LC" & var2 == "CHR GBC"){
    L <- perm_cor_brain_map(map1=netho_chr_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_chr_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_R, method="pearson")
  }else if(var1== "CHR BSV" & var2 == "CHR GBC"){
    L <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=gbc_chr_lms, bsmash2=gbc_chr_bsmash_R, method="pearson")
  }else if(var1== "22q GBC" & var2 == "CHR LC"){
    L <- perm_cor_brain_map(map1=gbc_22q_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_22q_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_R, method="pearson")
  }else if(var1== "22q LC" & var2 == "CHR LC"){
    L <- perm_cor_brain_map(map1=netho_22q_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_22q_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_R, method="pearson")
  }else if(var1== "22q BSV" & var2 == "CHR LC"){
    L <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_R, method="pearson")
  }else if(var1== "CHR GBC" & var2 == "CHR LC"){
    L <- perm_cor_brain_map(map1=gbc_chr_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_chr_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_R, method="pearson")
  }else if(var1== "CHR BSV" & var2 == "CHR LC"){
    L <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_chr_lms, map2=netho_chr_lms, bsmash2=netho_chr_bsmash_R, method="pearson")
  }else if(var1== "22q GBC" & var2 == "CHR BSV"){
    L <- perm_cor_brain_map(map1=gbc_22q_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_22q_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_R, method="pearson")
  }else if(var1== "22q LC" & var2 == "CHR BSV"){
    L <- perm_cor_brain_map(map1=netho_22q_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_22q_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_R, method="pearson")
  }else if(var1== "22q BSV" & var2 == "CHR BSV"){
    L <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=rsfa_22q_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_R, method="pearson")
  }else if(var1== "CHR GBC" & var2 == "CHR BSV"){
    L <- perm_cor_brain_map(map1=gbc_chr_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=gbc_chr_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_R, method="pearson")
  }else if(var1== "CHR LC" & var2 == "CHR BSV"){
    L <- perm_cor_brain_map(map1=netho_chr_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_L, method="pearson")
    R <- perm_cor_brain_map(map1=netho_chr_lms, map2=rsfa_chr_lms, bsmash2=rsfa_chr_bsmash_R, method="pearson")
  }else if(var1== var2){
    L <- list(true_correlation=1, nulls=rep(NA,times=10000))
    R <- list(true_correlation=1, nulls=rep(NA,times=10000))
  }
  # average left and right correlations, and concat nulls
  out <- list(true_correlation=mean(L$true_correlation, R$true_correlation), nulls=c(L$nulls, R$nulls))
  return(out)
}

cor_stats <- list()
for(i in 1: nrow(maps_all_df)){
  cor <- get_bilat_cor(maps_all_df[i,"Var1"], maps_all_df[i,"Var2"])
  maps_all_df[i,"value"] <- cor$true_correlation
  cor_stats[[i]] <- cor
}

# get p-values
for(i in 1: nrow(maps_all_df)){
  maps_all_df[i,"p"] <- perm_p(test_stat = cor_stats[[i]]$true_correlation, nulls=cor_stats[[i]]$nulls, alternative = "two.sided")
}

# threshold for p<0.05
maps_all_df$value_p05 <- maps_all_df$value
maps_all_df[which(maps_all_df$p>0.05),"value_p05"] <- NA

# get lower triangle
concat_names <- function(name1,name2){
 sorted <- sort(c(name1,name2), decreasing=F)
 new_col <- paste(sorted[1],sorted[2],sep="_")
 return(new_col)
}

# mark upper and lower triangle
for(i in 1:nrow(maps_all_df)){
 maps_all_df[i,"sort_col"] <- concat_names(maps_all_df[i,"Var1"], maps_all_df[i,"Var2"])
}

maps_all_df$tri <- "upper"
maps_all_df[which(maps_all_df$Var1 == maps_all_df$Var2),"tri"] <- "diag"
dup_indices <- which(duplicated(maps_all_df$sort_col))
maps_all_df[dup_indices,"tri"] <- "lower"

# replace lower triangle p-values values with upper
maps_upper_df <- filter(maps_all_df, tri=="upper")
maps_upper_df <- maps_upper_df[order(maps_upper_df$sort_col),]
maps_upper_df$value_p05 <- maps_upper_df$value

maps_lower_df <- filter(maps_all_df, tri=="lower")
maps_lower_df <- maps_lower_df[order(maps_lower_df$sort_col),]
maps_lower_df$p <- maps_upper_df$p
maps_lower_df[which(maps_lower_df$p > 0.05),"value_p05"] <- NA
maps_lower_df$value <- NA

maps_replace <- rbind(maps_upper_df,maps_lower_df, filter(maps_all_df, tri=="diag")) 

hmap_cor <- ggplot(maps_replace, aes(x=Var1,y=Var2))+
  theme_void(base_size = 13)+
  geom_tile(aes(fill=value), color="black")+
  geom_point(aes(color=value_p05, shape=!is.na(value_p05)),size=17)+
  scale_shape_manual(values=c(NA,19), labels=c("p > 0.05","p < 0.05"))+
  scale_fill_scico(palette="vik",limits=c(-0.6,0.6),na.value="white")+
  scale_color_scico(palette="vik",limits=c(-0.6,0.6),na.value="white")+
  scale_size(range = c(2,12))+
  theme(axis.text.x = element_text(angle = 20, hjust=0.5, size=18),
        axis.text.y = element_text(size=18),
        legend.position="right",
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        title = element_text(size=16),
        axis.title.x= element_text(size=19, vjust=-1),
        axis.title.y = element_text(angle = 0, vjust = 0.5, size=19),
        plot.margin = margin(0.5,0.1,0.1,0.1, "in"))+
  ylab("map 2")+
  xlab("map 1")+
  #scale_y_discrete(position = "right")+
  ggtitle("Correlations between fMRI case-control maps")+
  guides(fill = guide_colourbar(order = 2, title="Pearson's r"),
         color = "none",
         shape = guide_legend(order=1, title="Significance\n(upper triangle)", ,frame.colour = "black", frame.linewidth = 20))
plot(hmap_cor)

if(save_outputs==TRUE){
  ggsave(plot=hmap_cor, filename = file.path(project,"figures/fmri_maps/correlation_heatmap.pdf"), device="pdf", width=7.5, height=5.5)
}

# plot distributions for two significant pairs
cor_nulls1 <- plot_cor_nulls(test_stat=cor_stats[[which(maps_all_df$Var1 == "22q BSV" & maps_all_df$Var2 == "22q LC")]]$true_correlation, nulls=cor_stats[[which(maps_all_df$Var1 == "22q BSV" & maps_all_df$Var2 == "22q LC")]]$nulls, xlab="Pearson's r", title="22qDel LC vs. 22qDel BSV")

cor_nulls2 <- plot_cor_nulls(test_stat=cor_stats[[which(maps_all_df$Var1 == "CHR LC" & maps_all_df$Var2 == "22q GBC")]]$true_correlation, nulls=cor_stats[[which(maps_all_df$Var1 == "CHR LC" & maps_all_df$Var2 == "22q GBC")]]$nulls, xlab="Pearson's r", title="22qDel GBC vs. CHR LC", alternative = "two.sided")

cor_nulls_all <- cor_nulls1+cor_nulls2+ 
  plot_annotation(title = 'Null distributions for significant comparisons',theme=theme(plot.title=element_text(size=16,hjust=0.5)))
cor_nulls_all
if(save_outputs==TRUE){
  ggsave(plot=cor_nulls_all, filename = file.path(project,"figures/fmri_maps/correlations_null_dist.pdf"), device="pdf", width=7, height=4)
}
 

# plot_cor_nulls(test_stat=netho_rsfa_22q_cor_R$true_correlation, nulls=netho_rsfa_22q_cor_R$nulls, xlab="Pearson r", title="NetHo vs RSFA, RH")
# #plot_cor_nulls(rsfa_netho_22q_cor_L, title="RSFA vs NetHo, LH, n=10,000")
# #plot_cor_nulls(rsfa_netho_22q_cor_R, title="RSFA vs NetHo, RH, n=10,000")
# plot_cor_nulls(test_stat=gbc_rsfa_22q_cor_L$true_correlation, nulls=gbc_rsfa_22q_cor_L$nulls, xlab="Pearson r", title="GBC vs RSFA, LH")
# plot_cor_nulls(test_stat=gbc_rsfa_22q_cor_R$true_correlation, nulls=gbc_rsfa_22q_cor_R$nulls, xlab="Pearson r", title="GBC vs RSFA, RH")
# plot_cor_nulls(test_stat=gbc_netho_22q_cor_L$true_correlation, nulls=gbc_netho_22q_cor_L$nulls, xlab="Pearson r", title="GBC vs NetHo, LH")
# plot_cor_nulls(test_stat=gbc_netho_22q_cor_R$true_correlation, nulls=gbc_netho_22q_cor_R$nulls, xlab="Pearson r", title="GBC vs NetHo, RH")
# 

```

make heatmap comparing control groups
```{r plotPermCorControl}

ctrl_maps_all <- c("Control22q GBC","Control22q LC","Control22q BSV","ControlCHR GBC", "ControlCHR LC", "ControlCHR BSV")  
#maps_all_df <- expand.grid(maps_all,maps_all) %>% filter(., Var1 != Var2)
ctrl_maps_all_df <- expand.grid(ctrl_maps_all,ctrl_maps_all)


get_bilat_cor_ctrl <- function(var1, var2){
if(var1 == "Control22q LC" & var2 == "Control22q GBC"){
    L <- perm_cor_brain_map(map1=control_22q_netho, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_netho, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")
  }else if(var1 == "Control22q BSV" & var2 == "Control22q GBC"){
    L <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR GBC" & var2 == "Control22q GBC"){
    L <- perm_cor_brain_map(map1=control_n_gbc, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_gbc, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR LC" & var2 == "Control22q GBC"){
    L <- perm_cor_brain_map(map1=control_n_netho, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_netho, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR BSV" & var2 == "Control22q GBC"){
    L <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_22q_gbc, bsmash2=gbc_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q GBC" & var2 == "Control22q LC"){
    L <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q BSV" & var2 == "Control22q LC"){
    L <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR GBC" & var2 == "Control22q LC"){
    L <- perm_cor_brain_map(map1=control_n_gbc, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_gbc, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR LC" & var2 == "Control22q LC"){
    L <- perm_cor_brain_map(map1=control_n_netho, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_netho, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR BSV" & var2 == "Control22q LC"){
    L <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_22q_netho, bsmash2=netho_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q GBC" & var2 == "Control22q BSV"){
    L <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q LC" & var2 == "Control22q BSV"){
    L <- perm_cor_brain_map(map1=control_22q_netho, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_netho, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR GBC" & var2 == "Control22q BSV"){
    L <- perm_cor_brain_map(map1=control_n_gbc, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_gbc, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR LC" & var2 == "Control22q BSV"){
    L <- perm_cor_brain_map(map1=control_n_netho, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_netho, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR BSV" & var2 == "Control22q BSV"){
    L <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_22q_rsfa, bsmash2=rsfa_control_22q_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q GBC" & var2 == "ControlCHR GBC"){
    L <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q LC" & var2 == "ControlCHR GBC"){
    L <- perm_cor_brain_map(map1=control_22q_netho, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_netho, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q BSV" & var2 == "ControlCHR GBC"){
    L <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR LC" & var2 == "ControlCHR GBC"){
    L <- perm_cor_brain_map(map1=control_n_netho, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_netho, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR BSV" & var2 == "ControlCHR GBC"){
    L <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_n_gbc, bsmash2=gbc_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q GBC" & var2 == "ControlCHR LC"){
    L <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_n_netho, bsmash2=netho_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_n_netho, bsmash2=netho_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value") 
  }else if(var1 == "Control22q LC" & var2 == "ControlCHR LC"){
    L <- perm_cor_brain_map(map1=control_22q_netho, map2=control_n_netho, bsmash2=netho_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_netho, map2=control_n_netho, bsmash2=netho_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q BSV" & var2 == "ControlCHR LC"){
    L <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_n_netho, bsmash2=netho_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_n_netho, bsmash2=netho_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR GBC" & var2 == "ControlCHR LC"){
    L <- perm_cor_brain_map(map1=control_n_gbc, map2=control_n_netho, bsmash2=netho_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_gbc, map2=control_n_netho, bsmash2=netho_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR BSV" & var2 == "ControlCHR LC"){
    L <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_n_netho, bsmash2=netho_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_rsfa, map2=control_n_netho, bsmash2=netho_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q GBC" & var2 == "ControlCHR BSV"){
    L <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_gbc, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q LC" & var2 == "ControlCHR BSV"){
    L <- perm_cor_brain_map(map1=control_22q_netho, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_netho, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "Control22q BSV" & var2 == "ControlCHR BSV"){
    L <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_22q_rsfa, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value") 
  }else if(var1 == "ControlCHR GBC" & var2 == "ControlCHR BSV"){
    L <- perm_cor_brain_map(map1=control_n_gbc, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_gbc, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")  
  }else if(var1 == "ControlCHR LC" & var2 == "ControlCHR BSV"){
    L <- perm_cor_brain_map(map1=control_n_netho, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_L, method="pearson", val_col1="value", val_col2="value")
    R <- perm_cor_brain_map(map1=control_n_netho, map2=control_n_rsfa, bsmash2=rsfa_control_n_bsmash_R, method="pearson", val_col1="value", val_col2="value")    
  }else if(var1== var2){
    L <- list(true_correlation=1, nulls=rep(NA,times=10000))
    R <- list(true_correlation=1, nulls=rep(NA,times=10000))
  }
  # average left and right correlations, and concat nulls
  out <- list(true_correlation=mean(L$true_correlation, R$true_correlation), nulls=c(L$nulls, R$nulls))
  return(out)
}


ctrl_cor_stats <- list()
for(i in 1: nrow(ctrl_maps_all_df)){
  ctrl_cor <- get_bilat_cor_ctrl(ctrl_maps_all_df[i,"Var1"],ctrl_maps_all_df[i,"Var2"])
  ctrl_maps_all_df[i,"value"] <- ctrl_cor$true_correlation
  ctrl_cor_stats[[i]] <- ctrl_cor
}

# get p-values
# TO DO: nulls empty
for(i in 1: nrow(ctrl_maps_all_df)){
  ctrl_maps_all_df[i,"p"] <- perm_p(test_stat = ctrl_cor_stats[[i]]$true_correlation, nulls=ctrl_cor_stats[[i]]$nulls, alternative = "two.sided")
}

# threshold for p<0.05
ctrl_maps_all_df$value_p05 <- ctrl_maps_all_df$value
ctrl_maps_all_df[which(ctrl_maps_all_df$p>0.05),"value_p05"] <- NA

# get lower triangle
concat_names <- function(name1,name2){
 sorted <- sort(c(name1,name2), decreasing=F)
 new_col <- paste(sorted[1],sorted[2],sep="_")
 return(new_col)
}

# mark upper and lower triangle
for(i in 1:nrow(ctrl_maps_all_df)){
 ctrl_maps_all_df[i,"sort_col"] <- concat_names(ctrl_maps_all_df[i,"Var1"], ctrl_maps_all_df[i,"Var2"])
}

ctrl_maps_all_df$tri <- "upper"
ctrl_maps_all_df[which(ctrl_maps_all_df$Var1 == ctrl_maps_all_df$Var2),"tri"] <- "diag"
ctrl_dup_indices <- which(duplicated(ctrl_maps_all_df$sort_col))
ctrl_maps_all_df[ctrl_dup_indices,"tri"] <- "lower"

# replace lower triangle p-values values with upper
ctrl_maps_upper_df <- filter(ctrl_maps_all_df, tri=="upper")
ctrl_maps_upper_df <- ctrl_maps_upper_df[order(ctrl_maps_upper_df$sort_col),]
ctrl_maps_upper_df$value_p05 <- ctrl_maps_upper_df$value

ctrl_maps_lower_df <- filter(ctrl_maps_all_df, tri=="lower")
ctrl_maps_lower_df <- ctrl_maps_lower_df[order(ctrl_maps_lower_df$sort_col),]
ctrl_maps_lower_df$p <- ctrl_maps_upper_df$p
ctrl_maps_lower_df[which(ctrl_maps_lower_df$p > 0.05),"value_p05"] <- NA
ctrl_maps_lower_df$value <- NA

ctrl_maps_replace <- rbind(ctrl_maps_upper_df, ctrl_maps_lower_df, filter(ctrl_maps_all_df, tri=="diag")) 
ctrl_maps_replace[which(ctrl_maps_replace[,"tri"]=="diag"),c("value","value_p05")] <- NA

ctrl_hmap_cor <- ggplot(ctrl_maps_replace, aes(x=Var1,y=Var2))+
  theme_void(base_size = 13)+
  geom_tile(aes(fill=value), color="black")+
  geom_point(aes(color=value_p05, shape=!is.na(value_p05)),size=19)+
  scale_shape_manual(values=c(NA,19), labels=c("p > 0.05","p < 0.05"))+
  scale_fill_scico(palette="vik",limits=c(-1,1),na.value="white")+
  scale_color_scico(palette="vik",limits=c(-1,1),na.value="white")+
  scale_size(range = c(2,12))+
  theme(axis.text.x = element_text(angle = 25, hjust=1, vjust=1, size=18),
        axis.text.y = element_text(size=18),
        legend.position="right",
        legend.title = element_text(size=16),
        legend.text = element_text(size=14),
        title = element_text(size=16),
        axis.title.x= element_text(size=19, vjust=-1),
        axis.title.y = element_text(angle = 0, vjust = 0.5, size=19),
        plot.margin = margin(0.5,0.1,0.1,0.1, "in"))+
  ylab("map 2")+
  xlab("map 1")+
  #scale_y_discrete(position = "right")+
  ggtitle("Correlations between fMRI control maps")+
  guides(fill = guide_colourbar(order = 2, title="Pearson's r"),
         color = "none",
         shape = guide_legend(order=1, title="Significance\n(upper triangle)", ,frame.colour = "black", frame.linewidth = 20))
plot(ctrl_hmap_cor)

if(save_outputs==TRUE){
  ggsave(plot=ctrl_hmap_cor, filename = file.path(project,"figures/fmri_maps/control_correlation_heatmap.pdf"), device="pdf", width=11, height=7.5)
  ggsave(plot=ctrl_hmap_cor, filename = file.path(project,"figures/fmri_maps/control_correlation_heatmap.png"), device="png", width=11, height=7.5, bg="white")
}

# # plot distributions for two significant pairs
# cor_nulls1 <- plot_cor_nulls(test_stat=cor_stats[[which(maps_all_df$Var1 == "22q LC" & maps_all_df$Var2 == "22q BSV")]]$true_correlation, nulls=cor_stats[[which(maps_all_df$Var1 == "22q LC" & maps_all_df$Var2 == "22q BSV")]]$nulls, xlab="Pearson's r", title="22qDel LC vs. 22qDel BSV")
# 
# cor_nulls2 <- plot_cor_nulls(test_stat=cor_stats[[which(maps_all_df$Var1 == "22q GBC" & maps_all_df$Var2 == "CHR LC")]]$true_correlation, nulls=cor_stats[[which(maps_all_df$Var1 == "22q GBC" & maps_all_df$Var2 == "CHR LC")]]$nulls, xlab="Pearson's r", title="22qDel GBC vs. CHR LC")
# 
# cor_nulls_all <- cor_nulls1+cor_nulls2+ 
#   plot_annotation(title = 'Null distributions for significant comparisons',theme=theme(plot.title=element_text(size=16,hjust=0.5)))
# cor_nulls_all
# if(save_outputs==TRUE){
#   ggsave(plot=cor_nulls_all, filename = file.path(project,"figures/fmri_maps/correlations_null_dist.pdf"), device="pdf", width=7, height=4)
# }


```

read AHBA data
```{r readAHBA}
# load parcellated AHBA data
# this csv is the output of abagen.get_expression_data() python function to extract AHBA expression from CAB-NP surface atlas
# https://abagen.readthedocs.io/en/stable/user_guide/expression.html
ahbaSurfCABNP <- read.csv(file.path(project,"CAB-NP_surface_abagen_expression.csv"), header=T, sep=",") %>% rename("INDEX"="label")

ahbaSurfCABNP_L <- filter(ahbaSurfCABNP, INDEX <= 180)
ahbaSurfCABNP_R <- filter(ahbaSurfCABNP, INDEX > 180 & INDEX <= 360)
```

AHBA partial least squares
```{r plsAHBA}
# # function to compare chosen brain map to AHBA with PLS
# ahba_pls <- function(ahba=ahbaSurfCABNP_L, map, val_col, verbose=FALSE){
#   if(verbose==TRUE){print(val_col)}
#   indices <- ahba$INDEX
#   # get list of genes
#   genes <- names(ahba)[which(names(ahba) != "INDEX")]
#   # filter for only rois in ahba data and merge
#   fmap <- filter(map, INDEX %in% indices)[,c("INDEX", val_col)]
#   df <- merge(x=ahba, y=fmap, by="INDEX") 
#   # make pls formula with val_col on left and all genes on right
#   xcols <- paste(genes, collapse=" + ")
#   plsformula <- as.formula(paste(val_col,"~", xcols))
#   # test model with k-fold cross validation using 6 segments
#   pls_test <- plsr(formula=plsformula, data=df, scale=TRUE, center=TRUE, validation="CV", na.action="na.omit", segments=6)
# }
# 
# # function to return first component Y R2 from pls model
# # chose components with ncomp, default is just first component
# get_yr2 <- function(input, ncomp=1, estimate="CV"){
#   out <- R2(input, estimate = estimate, intercept = FALSE, ncomp=ncomp)$val %>% drop
#   return(out)
# }
# 
# rsfsa_ahba_pls <- ahba_pls(map=rsfa_22q_lms, val_col="beta")
# 
# #validationplot(rsfsa_ahba_pls,ncomp =1:5, val.type = "R2")
# #validationplot(rsfsa_ahba_pls,ncomp =1:5, val.type = "RMSEP")
# #validationplot(rsfsa_ahba_pls,ncomp =1:5, val.type = "MSEP")
# 
# # x and y total variance explained
# # https://stackoverflow.com/questions/55380244/how-to-get-y-variance-explained-from-a-pls-model
# #y_r2 <- R2(rsfsa_ahba_pls, estimate = "CV", intercept = FALSE, ncomp=1:5)$val %>% drop 
# rsfa_y_r2 <- get_yr2(input=rsfsa_ahba_pls, ncomp=1:5)
# rsfa_x_r2 <- cumsum(explvar(rsfsa_ahba_pls))[1:5]/100
# 
# gbc_ahba_pls <- ahba_pls(map=gbc_22q_lms, val_col="beta")
# gbc_y_r2 <- get_yr2(input=gbc_ahba_pls, ncomp=1:5)
# gbc_x_r2 <- cumsum(explvar(gbc_ahba_pls))[1:5]/100
```

takes too long to compute permutations locally
on hoffman, clone this git repo and run submit_ahba_permute_hoffman.sh to submit as array
```{r}
# # function to compute PLS and brainSMASH permutation test with Y R2 as test statistic
# # default n=10,000 permutations (expects brainsmash columns named V1:V10000)
# # option for parallel computation, defaults to all cores
# # TODO: parallel failing for mc.cores>1
# # calculates 1-tailed p-value based on how many test stats from the null distribution are greater than the true test stat
# ahba_permute_pls <- function(map, val_col, bsmash, cols=paste0("V",1:10000), verbose=FALSE, parallel=TRUE){
#   # first test pls model with true brain map
#   pls <- ahba_pls(map=map, val_col=val_col, verbose=verbose)
#   # get test statistic for true model
#   test_stat <- get_yr2(input=pls, ncomp=1, estimate="CV")
#   # compute permuted test stats
#   nulls <- NULL
#   for(i in 1:length(cols)){
#     col <- cols[i]
#     # print message on the same line for each loop
#     if(verbose==TRUE){
#       cat(col,"...",(i/length(cols)*100),"%","\r")
#       flush.console()
#     }
#     #print(paste(col,"...",(i/length(cols)*100),"%"))
#     null_mod <- ahba_pls(map=bsmash, val_col=col,verbose=FALSE)
#     null <- get_yr2(input=null_mod, ncomp=1, estimate="CV")
#     nulls <- c(nulls, null)
#   }
#   # get 1-tailed p-value
#   p <- sum(nulls > test_stat)/length(nulls)
#   # return as list with original pls model, test statistic (first component Y R2), null test statistics, and 1-tailed p-value 
#   out <- list(pls=pls, test_stat=test_stat, nulls=nulls, pval=p)
#   return(out)
# }
# 
# # test with only a couple permutations  
# #rsfsa_ahba_perm_test <- ahba_permute_pls(map=rsfa_22q_lms, val_col="beta", bsmash=rsfa_22q_bsmash_L, cols=paste0("V",1:2), parallel=FALSE, verbose=TRUE)
# 
# # RSFA PLS for n=1,000 permutations
# rsfsa_ahba_perm <- ahba_permute_pls(map=rsfa_22q_lms, val_col="beta", bsmash=rsfa_22q_bsmash_L, cols=paste0("V",1:1000), parallel=FALSE, verbose=TRUE)
# 
#  
```

get permuted PLS p-value
```{r}
# # read nulls
# rsfa_nulls <- read.csv(file.path(project,"rsfa_ahba_pls_permuted_yr2.csv"))
# netho_nulls <- read.csv(file.path(project,"netho_ahba_pls_permuted_yr2.csv"))
# gbc_nulls <- read.csv(file.path(project,"gbc_ahba_pls_permuted_yr2.csv"))
# 
# # plot distributions
# plot_cor_nulls(test_stat = rsfa_y_r2[1], nulls=as.numeric(rsfa_nulls[1,]), alternative = "greater", xlab="Comp 1 Y R2", title="RSFA vs AHBA")
# plot_cor_nulls(test_stat = gbc_y_r2[1], nulls=as.numeric(gbc_nulls[1,]), alternative = "greater", xlab="Comp 1 Y R2", title="GBC vs AHBA")
```

```{r bmapCor}
# function to correlate two brain maps
# map1 and map2 should be same length vectors corresponding to the same parcels
cor_brain_maps <- function(map1, map2, method="pearson", use="complete.obs"){
  cor <- cor(x=as.numeric(map1), y=as.numeric(map2), use=use, method=method) %>% as.numeric
  return(cor)
}

cor_brain_ahba <- function(ahba=ahbaSurfCABNP_L, map, gene, val_col, verbose=FALSE){
  if(verbose==TRUE){print(gene)}
  indices <- ahba$INDEX
  # filter for only rois in ahba data and merge
  fmap <- filter(map, INDEX %in% indices)[,c("INDEX", val_col)]
  df <- merge(x=ahba, y=fmap, by="INDEX")
  out <- cor_brain_maps(map1=df[,val_col], map2=df[,gene]) %>% as.numeric
  return(out)
}

cor_brain_ahba_all <- function(ahba=ahbaSurfCABNP_L, map, val_col="group_beta", verbose=FALSE){
  # get list of genes
  genes <- names(ahba)[which(names(ahba) != "INDEX")]
  cors <- lapply(genes, function(g) cor_brain_ahba(gene=g, map=map, val_col=val_col, verbose=verbose)) %>% unlist
  out <- data.frame(gene=genes, cor=cors)
  return(out)
}
```

univariate AHBA correlations
```{r}
# # get AHBA correlations
# rsfa_ahba_cor <- cor_brain_ahba_all(map=rsfa_22q_lms, verbose=FALSE)
# #plot_cor_nulls(test_stat = 0.1, nulls=rsfa_ahba_cor$cor, alternative = "greater")
# netho_ahba_cor <- cor_brain_ahba_all(map=netho_22q_lms, verbose=FALSE)
# gbc_ahba_cor <- cor_brain_ahba_all(map=gbc_22q_lms, verbose=FALSE)
# 
# # write.table(rsfa_ahba_cor, file=file.path(project,"CAB-NP/22q_TD_RSFA_AHBA.csv"), quote=FALSE, row.names = FALSE, sep=",")
# # write.table(netho_ahba_cor, file=file.path(project,"CAB-NP/22q_TD_NetHo_AHBA.csv"), quote=FALSE,  row.names = FALSE, sep=",")
# # write.table(gbc_ahba_cor, file=file.path(project,"CAB-NP/22q_TD_GBC_AHBA.csv"), quote=FALSE, row.names = FALSE, sep=",")
```

```{r}
# # get top 10% absolute value of connections
# get_quantile <- function(data,probs=0.90,alternative="two.sided"){
#   if(alternative=="two.sided"){
#     data <- abs(data)
#   }
#   out <- as.numeric(quantile(data, probs=probs))
# }
# 
# # to be run on the output of rsfa_ahba_cor
# get_quantile_genes <- function(df,probs=0.90,alternative="two.sided"){
#   # get correlation value for cutoff
#   threshold <- get_quantile(data=df$cor, probs=probs, alternative=alternative)
#   # get gene names past cutoff
#   if(alternative=="two.sided"){
#     genes <- df[which(abs(df$cor) > threshold),"gene"]
#   }else if(alternative=="greater"){
#     genes <- df[which(df$cor > threshold),"gene"]
#   }else if(alternative=="less"){
#     genes <- df[which(df$cor < threshold),"gene"]
#   }
#   return(genes)
# }
# 
# # get top 90th percentile of absolute value correlations for RSFA
# rsfa_ahba_abs90 <- get_quantile_genes(df=rsfa_ahba_cor, probs=0.90, alternative="two.sided")
# rsfa_ahba_abs95 <- get_quantile_genes(df=rsfa_ahba_cor, probs=0.95, alternative="two.sided")
```

calculates 2-tailed p-value based on how many test stats from the null distribution are greater than the true test stat
```{r mapPermuteCor}
# permutation correlation 
map_permute_cor <- function(map, variable, bsmash, bsmash_cols=paste0("V",1:10000), verbose=FALSE, method="pearson", use="complete.obs"){
  if(verbose==TRUE){print(variable)}
  # error if bsmash and ahba have overlapping column names
  #if(sum(names(bsmash) %in% names(map) & names(bsmash) != "INDEX") != 0){stop("Error: bsmash and ahba have overlapping column names")}
  indices <- map$INDEX
  df <- merge(x=map, y=bsmash, by="INDEX") %>% as.data.frame
  # compute permuted test stats
  nulls <- NULL
  for(i in 1:length(bsmash_cols)){
    col <- bsmash_cols[i]
    # print message on the same line for each loop
    if(verbose==TRUE){
      cat("\r",col,"...",(i/length(bsmash_cols)*100),"%","\r")
      flush.console()
    }
    null <- cor(x=as.numeric(df[,variable]), y=as.numeric(df[,col]), use=use, method=method) %>% as.numeric
    nulls <- c(nulls, null)
  }
  return(nulls)
}

# test with only a few permutations
#rsfa_ahba_abs95_nulls <- lapply(rsfa_ahba_abs95[1:10], function(g) ahba_permute_cor(gene=g, bsmash=rsfa_22q_bsmash_L, verbose=TRUE, bsmash_cols=paste0("V",1:10)))

#rsfa_ahba_abs95_nulls <- lapply(rsfa_ahba_abs95, function(g) ahba_permute_cor(variable=g,map=ahbaSurfCABNP_L, bsmash=rsfa_22q_bsmash_L, verbose=TRUE))
```

correlate case-control with neuromaps LH output
```{r neuromapCor}
# read data fromm Kuldeep
neuromaps <- read.csv(file.path(project,"df_neuromaps_Glasser180.csv"), header=TRUE) %>% rename("GlasserRegion"="X")
nmap_cols <- names(neuromaps)[which(names(neuromaps) !="GlasserRegion")]

# get PVALB-SST column in AHBA
ahbaSurfPVSST_L <- ahbaSurfCABNP_L
ahbaSurfPVSST_L$PVALB_SST <- ahbaSurfPVSST_L$PVALB - ahbaSurfPVSST_L$SST

# add size of ROIs
roi_sizes_L <- xii_Ji_parcel$data$cortex_left %>% table %>% as.data.frame
colnames(roi_sizes_L) <- c("INDEX","ROI_size")

# update nmap_cols
nmap_cols <- c(nmap_cols,"PVALB_SST","ROI_size")

# function to merge CAB-NP results with HCP parcel names
cabnp_hcp_lh <- function(hcp_df, colname="GlasserRegion", cabnp_df, ahba_df=ahbaSurfPVSST_L, ahba_cols="PVALB_SST", sizes=roi_sizes_L){
  lh <- filter(cabnp_df, INDEX %in% 1:180)
  lh$GLASSERLABELNAME
  lh[,colname] <- lh$GLASSERLABELNAME %>% gsub("^L_","",.) %>% gsub("_ROI","",.)
  out <- merge(x=lh, y=hcp_df, by=colname)
  out <- merge(x=out, y=sizes, by="INDEX")
  if(!is.null(ahba_df)){
    ahba_merge <- ahba_df[,c("INDEX",ahba_cols)]
    out <- merge(x=out, y=ahba_merge, by="INDEX")
  }
  return(out)
}

# merge with neuromap
rsfa_22q_nmap <- cabnp_hcp_lh(cabnp_df=rsfa_22q_lms, hcp_df=neuromaps)
netho_22q_nmap <- cabnp_hcp_lh(cabnp_df=netho_22q_lms, hcp_df=neuromaps)
gbc_22q_nmap <- cabnp_hcp_lh(cabnp_df=gbc_22q_lms, hcp_df=neuromaps)

rsfa_chr_nmap <- cabnp_hcp_lh(cabnp_df=rsfa_chr_lms, hcp_df=neuromaps)
netho_chr_nmap <- cabnp_hcp_lh(cabnp_df=netho_chr_lms, hcp_df=neuromaps)
gbc_chr_nmap <- cabnp_hcp_lh(cabnp_df=gbc_chr_lms, hcp_df=neuromaps)

# get neuromap df without fMRI result
neuromaps_ordered <- subset(data.table(rsfa_22q_nmap), select=-c(group_beta, group_FDR_q, group_FDR_sig, group_beta_FDR, group_se, group_t, group_p))

# correlate with nmap columns
nmap_cor <- function(map1, map_all, method="pearson", use="complete.obs", cols=nmap_cols){
  cor <- lapply(cols, function(c) cor_brain_maps(map1=map1, map2=map_all[,c], method=method, use=use)) %>% as.numeric
  out <- data.frame(map=cols, cor=cor)
  out$cor %<>% as.numeric
  out <- out[order(out$cor),]
  return(out)
}

rsfa_22q_nmap_cor <- nmap_cor(map1=rsfa_22q_nmap$group_beta, map_all=rsfa_22q_nmap, method="pearson", use="complete.obs")
netho_22q_nmap_cor <- nmap_cor(map1=netho_22q_nmap$group_beta, map_all=netho_22q_nmap, method="pearson", use="complete.obs")
gbc_22q_nmap_cor <- nmap_cor(map1=gbc_22q_nmap$group_beta, map_all=gbc_22q_nmap, method="pearson", use="complete.obs")

rsfa_chr_nmap_cor <- nmap_cor(map1=rsfa_chr_nmap$group_beta, map_all=rsfa_chr_nmap, method="pearson", use="complete.obs")
netho_chr_nmap_cor <- nmap_cor(map1=netho_chr_nmap$group_beta, map_all=netho_chr_nmap, method="pearson", use="complete.obs")
gbc_chr_nmap_cor <- nmap_cor(map1=gbc_chr_nmap$group_beta, map_all=gbc_chr_nmap, method="pearson", use="complete.obs")

# plot
# pl_cmruglu <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_nmap, roi_col="INDEX", val_col="cmruglu")
# view_xifti_surface(pl_cmruglu, title="Glucose Metabolism", cex.title=1.3, colors="magma",hemisphere="left")
# pl_rsfa_22q_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=rsfa_22q_lms, roi_col="INDEX", val_col="beta")
# view_xifti_surface(pl_rsfa_22q_b, title="Signal Variablity: 22qDel vs TD", cex.title=1.3,zlim=c(-0.8,0.8), colors=pal_red_blue(),hemisphere="left")

# bsmash permutations for neuromaps
#rsfa_22q_nmap_nulls <- map_permute_cor(map=neuromaps_ordered, variable="cmruglu", bsmash=rsfa_22q_bsmash_L, bsmash_cols=paste0("V",1:10000))

# test perm p for one measure
#perm_p(test_stat=rsfa_22q_nmap_cor[1,2], nulls=rsfa_22q_nmap_nulls, alternative="two.sided")

# function to compute nulls and perm-p for each neuromaps measure
# outputs list object containing neuromaps outputs with p-vals added, and a data frame with a column for each null and row for each measure
perm_p_neuromaps <- function(neuromap_outputs, order=nmap_match$variable, neuromap_df=neuromaps_ordered, bsmash, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE){
  maps <- neuromap_outputs$map
  nmap_out <- neuromap_outputs
  nmap_out$p <- NA
  null_df <- NULL
  for(m in maps){
    # get true correlation
    cor <- filter(neuromap_outputs, map==m)$cor
    # get nulls
    nulls <- map_permute_cor(map=neuromap_df, variable=m, bsmash=bsmash, bsmash_cols=bsmash_cols)
    # get p-val
    p <- perm_p(test_stat=cor, nulls=nulls, alternative=alternative)
    # record outputs
    nmap_out[which(nmap_out$map==m),"p"] <- p
    null_df <- cbind(null_df,nulls)
  }
  null_df %<>% as.data.frame
  colnames(null_df) <- maps
  null_df$perm <- 1:nrow(null_df)
  nmap_out %<>% as.data.frame
  nmap_out[match(order, nmap_out$map),]
  out <- list(pvals=as.data.frame(nmap_out), nulls=null_df)
  return(out)
}

# neuromaps permuted p-vals
nmap_match <- data.frame(variable=c("cmruglu", "cmr02", "CBF", "cbv", "PC1.AHBA", "PVALB_SST", "G1.fMRI", "intersubjvar", "PC1.Neurosynth", "scalingpnc", "scalingnih", "devexp", "Evolution.Expansion", "Cortical.Thickness", "T1T2ratio", "meg_delta", "meg_theta", "meg_alpha", "meg_beta", "meg_gamma1", "meg_gamma2","ROI_size"), name=c("Glucose metabolism", "Oxygen metabolism", "Cerebral blood flow", "Cerebral blood volume", "PC1 gene expression", "PVALB-SST gradient","fMRI gradient", "Intersubject variability", "PC1 neurosynth", "Allometric scaling (PNC)", "Allometric scaling (NIH)", "Developmental expansion", "Evolutionary expansion", "Cortical thickness", "T1w/T2w ratio", "MEG delta", "MEG theta", "MEG alpha", "MEG beta", "MEG gamma1", "MEG gamma2","ROI size"))
#nmap_order <- c("cmruglu","cmr02","CBF","cbv","G1.fMRI","intersubjvar","PC1.AHBA","PC1.Neurosynth","scalingpnc","scalingnih","devexp","Evolution.Expansion","Cortical.Thickness","T1T2ratio","meg_delta","meg_theta","meg_alpha","meg_beta","meg_gamma1","meg_gamma2")
# 22q
rsfa_22q_nmap_p <- perm_p_neuromaps(neuromap_outputs=rsfa_22q_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=rsfa_22q_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

netho_22q_nmap_p <- perm_p_neuromaps(neuromap_outputs=netho_22q_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=netho_22q_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

gbc_22q_nmap_p <- perm_p_neuromaps(neuromap_outputs=gbc_22q_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=gbc_22q_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

# chr
rsfa_chr_nmap_p <- perm_p_neuromaps(neuromap_outputs=rsfa_chr_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=rsfa_chr_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

netho_chr_nmap_p <- perm_p_neuromaps(neuromap_outputs=netho_chr_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=netho_chr_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

gbc_chr_nmap_p <- perm_p_neuromaps(neuromap_outputs=gbc_chr_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=gbc_chr_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)
```

plot 22q case-control LH neuromaps results
```{r plotNeuromap22q}
# create long dataframes to plot nulls
rsfa_22q_nuls_long <- melt.data.table(as.data.table(rsfa_22q_nmap_p$nulls), id.vars="perm")
rsfa_22q_nuls_long$variable <- factor(rsfa_22q_nuls_long$variable,levels=nmap_match$variable,ordered=TRUE)

netho_22q_nuls_long <- melt.data.table(as.data.table(netho_22q_nmap_p$nulls), id.vars="perm")
netho_22q_nuls_long$variable <- factor(netho_22q_nuls_long$variable,levels=nmap_match$variable,ordered=TRUE)

gbc_22q_nuls_long <- melt.data.table(as.data.table(gbc_22q_nmap_p$nulls), id.vars="perm")
gbc_22q_nuls_long$variable <- factor(gbc_22q_nuls_long$variable,levels=nmap_match$variable,ordered=TRUE)

# plot
gbc_box <- ggplot(data=gbc_22q_nuls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=gbc_22q_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")+
  theme(legend.position="none")

netho_box <- ggplot(data=netho_22q_nuls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=netho_22q_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")

rsfa_box <- ggplot(data=rsfa_22q_nuls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  #geom_half_violin(fill="grey50", side="r", ="lightgrey", side="r", lty="blank")+
  geom_point(data=rsfa_22q_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  xlab("Brain Map Comparison")+
  #xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match$name)

neuromaps_22q_bplots <- gbc_box/netho_box/rsfa_box+plot_layout(guides = "collect")
neuromaps_22q_bplots

if(save_outputs==TRUE){
  ggsave(neuromaps_22q_bplots, file=file.path(project,"figures/neuromaps/neuromaps_22q_correlations.pdf"), device = "pdf", height = 8, width = 9)
}
```

plot chr LH neuromaps
```{r plotNeuromapCHR}
# create long dataframes to plot nulls
rsfa_chr_nuls_long <- melt.data.table(as.data.table(rsfa_chr_nmap_p$nulls), id.vars="perm")
rsfa_chr_nuls_long$variable <- factor(rsfa_chr_nuls_long$variable,levels=nmap_match$variable,ordered=TRUE)

netho_chr_nuls_long <- melt.data.table(as.data.table(netho_chr_nmap_p$nulls), id.vars="perm")
netho_chr_nuls_long$variable <- factor(netho_chr_nuls_long$variable,levels=nmap_match$variable,ordered=TRUE)

gbc_chr_nuls_long <- melt.data.table(as.data.table(gbc_chr_nmap_p$nulls), id.vars="perm")
gbc_chr_nuls_long$variable <- factor(gbc_chr_nuls_long$variable,levels=nmap_match$variable,ordered=TRUE)

# plot
chr_gbc_box <- ggplot(data=gbc_chr_nuls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=gbc_chr_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","steelblue"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")+
  theme(legend.position="none")

chr_netho_box <- ggplot(data=netho_chr_nuls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=netho_chr_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","steelblue"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")+
  theme(legend.position="none")
  
chr_rsfa_box <- ggplot(data=rsfa_chr_nuls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  #geom_half_violin(fill="grey50", side="r", ="lightgrey", side="r", lty="blank")+
  geom_point(data=rsfa_chr_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3,alpha=0.5)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  scale_color_manual(values = c("tan","steelblue"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  xlab("Brain Map Comparison")+
  #xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match$name)

neuromaps_chr_bplots <- chr_gbc_box/chr_netho_box/chr_rsfa_box+plot_layout(guides = "collect")
neuromaps_chr_bplots

if(save_outputs==TRUE){
  ggsave(neuromaps_chr_bplots, file=file.path(project,"figures/neuromaps/neuromaps_chr_correlations.pdf"), device = "pdf", height = 8, width = 9)
}
```

plot chosen neuromaps
```{r plotNeuromapBrains}
# glucose
pl_glucose <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="cmruglu")
view_xifti_surface(pl_glucose, title="Glucose metabolism",hemisphere = "left", cex.title=3,zlim=c(3300,7300), colors="plasma")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_glucose, title="Glucose metabolism",hemisphere = "left", cex.title=3,zlim=c(3300,7300), colors="plasma", fname=file.path(project,"figures/neuromaps/glucose.png"),legend_embed=TRUE)
}

# oxygen
pl_oxygen <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="cmr02")
view_xifti_surface(pl_oxygen, title="Oxygen metabolism",hemisphere = "left", cex.title=3,zlim=c(2200,6000), colors="plasma")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_oxygen, title="Oxygen metabolism",hemisphere = "left", cex.title=3,zlim=c(2200,6000), colors="plasma", fname=file.path(project,"figures/neuromaps/oxygen.png"),legend_embed=TRUE)
}

# CBF
pl_cbf <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="CBF")
view_xifti_surface(pl_cbf, title="Blood flow",hemisphere = "left", cex.title=3,zlim=c(10,70), colors="rocket")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_cbf, title="Blood flow",hemisphere = "left", cex.title=3,zlim=c(10,70), colors="rocket", fname=file.path(project,"figures/neuromaps/CBF.png"),legend_embed=TRUE)
}

# CBV
pl_cbv <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="cbv")
view_xifti_surface(pl_cbv, title="Blood volume",hemisphere = "left", cex.title=3,zlim=c(3000,7000), colors="rocket")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_cbv, title="Blood volume",hemisphere = "left", cex.title=3,zlim=c(3000,7000), colors="rocket", fname=file.path(project,"figures/neuromaps/CBV.png"),legend_embed=TRUE)
}

# G1 FMRI
pl_g1fmri <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="G1.fMRI")
view_xifti_surface(pl_g1fmri, title="fMRI gradient",hemisphere = "left", cex.title=3,zlim=c(-6.5,6.5), colors="viridis")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_g1fmri, title="fMRI gradient",hemisphere = "left", cex.title=3,zlim=c(-6.5,6.5), colors="viridis", fname=file.path(project,"figures/neuromaps/G1fMRI.png"),legend_embed=TRUE)
}

# intersubject
pl_inter <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="intersubjvar")
view_xifti_surface(pl_inter, title="Individual variation",hemisphere = "left", cex.title=3,zlim=c(0.4,0.7), colors="viridis")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_inter, title="Individual variation",hemisphere = "left", cex.title=3,zlim=c(0.4,0.7), colors="viridis", fname=file.path(project,"figures/neuromaps/intersubj.png"),legend_embed=TRUE)
}

# PVALB-SST
pl_pv <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="PVALB_SST")
view_xifti_surface(pl_pv, title="PVALB-SST gradient",hemisphere = "left", cex.title=3,zlim=c(-0.6,0.6), colors="viridis")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_pv, title="PVALB-SST gradient",hemisphere = "left", cex.title=3,zlim=c(-0.6,0.6), colors="viridis", fname=file.path(project,"figures/neuromaps/pvalb_sst.png"),legend_embed=TRUE)
}

# Size
pl_size <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=as.data.frame(neuromaps_ordered), roi_col="INDEX", val_col="ROI_size")
view_xifti_surface(pl_size, title="ROI size",hemisphere = "left", cex.title=3,zlim=c(35,840), colors="mako")
#save
if(save_outputs==TRUE){
  view_xifti_surface(pl_size, title="ROI size",hemisphere = "left", cex.title=3,zlim=c(-0.6,0.6), colors="mako", fname=file.path(project,"figures/neuromaps/pvalb_size.png"),legend_embed=TRUE)
}

# plot group difference beta 
# 22q RSFA
if(save_outputs==TRUE){
  view_xifti_surface(pl_rsfa_22q_b,zlim=c(-0.8,0.8), colors=pal_red_blue(),cex.title=3, hemisphere="left",  fname=file.path(project,"figures/neuromaps//rsfa_22q_b_l.png"),legend_embed=TRUE,title="22qDel BSV")
}

# 22q NetHo
if(save_outputs==TRUE){
  view_xifti_surface(pl_netho_22q_b,zlim=c(-0.8,0.8), colors=pal_red_blue(),cex.title=3, hemisphere="left", fname=file.path(project,"figures/neuromaps//netho_22q_b_l.png"),legend_embed=TRUE, title="22qDel LC")
}
```

neuromaps LH info table 
```{r neuromapTable, message=FALSE, warning=FALSE, paged.print=FALSE}
nmap_table <- data.frame(Map=nmap_match$name)

# add description and citation column to input table with Map column
nmap_table_update <- function(df, map, modality, citation){
  out <- as.data.frame(df)
  out[which(out$Map==map),c("Modality", "Citation")] <- c(modality, citation)
  return(as.data.frame(out))
}

nmap_table <- nmap_table_update(df=nmap_table, map="Glucose metabolism", modality="PET", citation="Vaishnavi et al. 2010")
nmap_table <- nmap_table_update(df=nmap_table, map="Oxygen metabolism", modality="PET", citation="Vaishnavi et al. 2010")
nmap_table <- nmap_table_update(df=nmap_table, map="Cerebral blood flow", modality="PET", citation="Vaishnavi et al. 2010")
nmap_table <- nmap_table_update(df=nmap_table, map="Cerebral blood volume", modality="PET", citation="Vaishnavi et al. 2010")
nmap_table <- nmap_table_update(df=nmap_table, map="PC1 gene expression", modality="mRNA", citation="Markello et al. 2021")
nmap_table <- nmap_table_update(df=nmap_table, map="PVALB-SST gradient", modality="mRNA", citation="Markello et al. 2021")
nmap_table <- nmap_table_update(df=nmap_table, map="fMRI gradient", modality="fMRI", citation="Margulies et al. 2016")
nmap_table <- nmap_table_update(df=nmap_table, map="Intersubject variability", modality="fMRI", citation="Mueller et al. 2013")
nmap_table <- nmap_table_update(df=nmap_table, map="PC1 neurosynth", modality="fMRI", citation="Yarkoni et al. 2011")
nmap_table <- nmap_table_update(df=nmap_table, map="Allometric scaling (PNC)", modality="sMRI", citation="Reardon et al. 2018")
nmap_table <- nmap_table_update(df=nmap_table, map="Allometric scaling (NIH)", modality="sMRI", citation="Reardon et al. 2018")
nmap_table <- nmap_table_update(df=nmap_table, map="Developmental expansion", modality="sMRI", citation="Hill et al. 2010")
nmap_table <- nmap_table_update(df=nmap_table, map="Evolutionary expansion", modality="sMRI", citation="Hill et al. 2010")
nmap_table <- nmap_table_update(df=nmap_table, map="Cortical thickness", modality="sMRI", citation="Glasser et al. 2016")
nmap_table <- nmap_table_update(df=nmap_table, map="T1w/T2w ratio", modality="sMRI", citation="Glasser et al. 2016")
nmap_table <- nmap_table_update(df=nmap_table, map="MEG delta", modality="MEG", citation="Van Essen et al. 2013")
nmap_table <- nmap_table_update(df=nmap_table, map="MEG theta", modality="MEG", citation="Van Essen et al. 2013")
nmap_table <- nmap_table_update(df=nmap_table, map="MEG alpha", modality="MEG", citation="Van Essen et al. 2013")
nmap_table <- nmap_table_update(df=nmap_table, map="MEG beta", modality="MEG", citation="Van Essen et al. 2013")
nmap_table <- nmap_table_update(df=nmap_table, map="MEG gamma1", modality="MEG", citation="Van Essen et al. 2013")
nmap_table <- nmap_table_update(df=nmap_table, map="MEG gamma2", modality="MEG", citation="Van Essen et al. 2013")
nmap_table <- nmap_table_update(df=nmap_table, map="ROI size", modality="sMRI", citation="Glasser et al. 2016")

# output table
nmap_table_out <- nmap_table %>% gt() %>% 
  tab_style(style = cell_text(weight = "bold"),locations = list(cells_column_labels())) %>%
  cols_align(align="left", columns=everything())%>%
  tab_options(data_row.padding = px(1))

# fix to stop gtsave from erroring
# https://github.com/rstudio/gt/issues/1077
# https://stackoverflow.com/questions/73964325/error-in-sclose-attempt-to-apply-non-function-when-calling-gtsave
#f <- chromote::default_chromote_object()
#f$close()

if(save_outputs==TRUE){
  gtsave(nmap_table_out, filename = file.path(project,"figures/neuromaps/table2.png"))
  gtsave(nmap_table_out, filename = file.path(project,"figures/neuromaps/table2.docx"))
}
```

Test control means LH neuromaps
```{r neuromapCorCtrl}

# merge control means with key
control_22q_gbc_k <- merge(x=control_22q_gbc, y=ji_key, all.x=TRUE, all.y=FALSE, by="INDEX")
control_22q_netho_k <- merge(x=control_22q_netho, y=ji_key, all.x=TRUE, all.y=FALSE, by="INDEX")
control_22q_rsfa_k <- merge(x=control_22q_rsfa, y=ji_key, all.x=TRUE, all.y=FALSE, by="INDEX")

control_n_gbc_k <- merge(x=control_n_gbc, y=ji_key, all.x=TRUE, all.y=FALSE, by="INDEX")
control_n_netho_k <- merge(x=control_n_netho, y=ji_key, all.x=TRUE, all.y=FALSE, by="INDEX")
control_n_rsfa_k <- merge(x=control_n_rsfa, y=ji_key, all.x=TRUE, all.y=FALSE, by="INDEX")

# merge with neuromap
control_22q_gbc_nmap   <- cabnp_hcp_lh(cabnp_df=control_22q_gbc_k, hcp_df=neuromaps)
control_22q_netho_nmap <- cabnp_hcp_lh(cabnp_df=control_22q_netho_k, hcp_df=neuromaps)
control_22q_rsfa_nmap  <- cabnp_hcp_lh(cabnp_df=control_22q_rsfa_k, hcp_df=neuromaps)

control_n_gbc_nmap    <- cabnp_hcp_lh(cabnp_df=control_n_gbc_k, hcp_df=neuromaps)
control_n_netho_nmap  <- cabnp_hcp_lh(cabnp_df=control_n_netho_k, hcp_df=neuromaps)
control_n_rsfa_nmap   <- cabnp_hcp_lh(cabnp_df=control_n_rsfa_k, hcp_df=neuromaps)

# get correlations
control_22q_gbc_nmap_cor   <- nmap_cor(map1=control_22q_gbc_nmap$value, map_all=control_22q_gbc_nmap, method="pearson", use="complete.obs")  
control_22q_netho_nmap_cor <- nmap_cor(map1=control_22q_netho_nmap$value, map_all=control_22q_netho_nmap, method="pearson", use="complete.obs")  
control_22q_rsfa_nmap_cor  <- nmap_cor(map1=control_22q_rsfa_nmap$value, map_all=control_22q_rsfa_nmap, method="pearson", use="complete.obs")  

control_n_gbc_nmap_cor    <- nmap_cor(map1=control_n_gbc_nmap$value, map_all=control_n_gbc_nmap, method="pearson", use="complete.obs")      
control_n_netho_nmap_cor  <- nmap_cor(map1=control_n_netho_nmap$value, map_all=control_n_netho_nmap, method="pearson", use="complete.obs")    
control_n_rsfa_nmap_cor   <- nmap_cor(map1=control_n_rsfa_nmap$value, map_all=control_n_rsfa_nmap, method="pearson", use="complete.obs")    

# get pvals
control_22q_gbc_nmap_p <- perm_p_neuromaps(neuromap_outputs=control_22q_gbc_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=gbc_control_22q_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_22q_netho_nmap_p <- perm_p_neuromaps(neuromap_outputs=control_22q_netho_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=netho_control_22q_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_22q_rsfa_nmap_p <- perm_p_neuromaps(neuromap_outputs=control_22q_rsfa_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=rsfa_control_22q_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_n_gbc_nmap_p <- perm_p_neuromaps(neuromap_outputs=control_n_gbc_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=gbc_control_n_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)
   
control_n_netho_nmap_p  <- perm_p_neuromaps(neuromap_outputs=control_n_netho_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=netho_control_n_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_n_rsfa_nmap_p <- perm_p_neuromaps(neuromap_outputs=control_n_rsfa_nmap_cor, neuromap_df=neuromaps_ordered, bsmash=rsfa_control_n_bsmash_L, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)  

```

plot control LH neuromaps results
```{r plotNeuromap22q}
# create long dataframes to plot nulls
control_22q_gbc_nulls_long <- melt.data.table(as.data.table(control_22q_gbc_nmap_p$nulls), id.vars="perm")
control_22q_gbc_nulls_long$variable <- factor(control_22q_gbc_nulls_long$variable,levels=nmap_match$variable,ordered=TRUE)

control_22q_netho_nulls_long <- melt.data.table(as.data.table(control_22q_netho_nmap_p$nulls), id.vars="perm")
control_22q_netho_nulls_long$variable <- factor(control_22q_netho_nulls_long$variable,levels=nmap_match$variable,ordered=TRUE)

control_22q_rsfa_nulls_long <- melt.data.table(as.data.table(control_22q_rsfa_nmap_p$nulls), id.vars="perm")
control_22q_rsfa_nulls_long$variable <- factor(control_22q_rsfa_nulls_long$variable,levels=nmap_match$variable,ordered=TRUE)

control_n_gbc_nulls_long <- melt.data.table(as.data.table(control_n_gbc_nmap_p$nulls), id.vars="perm")
control_n_gbc_nulls_long$variable <- factor(control_n_gbc_nulls_long$variable,levels=nmap_match$variable,ordered=TRUE)

control_n_netho_nulls_long <- melt.data.table(as.data.table(control_n_netho_nmap_p$nulls), id.vars="perm")
control_n_netho_nulls_long$variable <- factor(control_n_netho_nulls_long$variable,levels=nmap_match$variable,ordered=TRUE)

control_n_rsfa_nulls_long <- melt.data.table(as.data.table(control_n_rsfa_nmap_p$nulls), id.vars="perm")
control_n_rsfa_nulls_long$variable <- factor(control_n_rsfa_nulls_long$variable,levels=nmap_match$variable,ordered=TRUE)


# plot
ctrl_22q_gbc_box <- ggplot(data=control_22q_gbc_nulls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_22q_gbc_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")
  #theme(legend.position="none")

ctrl_22q_netho_box <- ggplot(data=control_22q_netho_nulls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_22q_netho_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")

ctrl_22q_rsfa_box <- ggplot(data=control_22q_rsfa_nulls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_22q_rsfa_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match$name)


ctrl_n_gbc_box <- ggplot(data=control_n_gbc_nulls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_n_gbc_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")+
  theme(legend.position="none")

ctrl_n_netho_box <- ggplot(data=control_n_netho_nulls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_n_netho_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")

ctrl_n_rsfa_box <- ggplot(data=control_n_rsfa_nulls_long, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_n_rsfa_nmap_p$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  xlab("Brain Map Comparison")+
  #xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match$name)+
  theme(legend.position="none")

neuromaps_control_n_bplots <- ctrl_n_gbc_box/ctrl_n_netho_box/ctrl_n_rsfa_box+plot_layout(guides = "collect")
neuromaps_control_22q_bplots <- ctrl_22q_gbc_box/ctrl_22q_netho_box/ctrl_22q_rsfa_box+plot_layout(guides = "collect")
#neuromaps_control_bplots <- ctrl_22q_gbc_box/ctrl_n_gbc_box/ctrl_22q_netho_box/ctrl_n_netho_box/ctrl_22q_rsfa_box/ctrl_n_rsfa_box+plot_layout(guides = "collect")
#neuromaps_control_bplots <- ggarrange(neuromaps_control_22q_bplots, neuromaps_control_n_bplots, nrow=1)

if(save_outputs==TRUE){
  # ggsave(neuromaps_control_bplots, file=file.path(project,"figures/neuromaps/neuromaps_control_correlations.pdf"), device = "pdf", height = 12, width = 10)
  # ggsave(neuromaps_control_bplots, file=file.path(project,"figures/neuromaps/neuromaps_control_correlations.png"), device = "png", height = 12, width = 10)
  ggsave(neuromaps_control_22q_bplots, file=file.path(project,"figures/neuromaps/neuromaps_control22q_correlations.pdf"), device = "pdf", height = 8, width = 9)
  ggsave(neuromaps_control_22q_bplots, file=file.path(project,"figures/neuromaps/neuromaps_control22q_correlations.png"), device = "png", height = 8, width = 9)

  ggsave(neuromaps_control_n_bplots, file=file.path(project,"figures/neuromaps/neuromaps_controlCHR_correlations.pdf"), device = "pdf", height = 8, width = 9)
  ggsave(neuromaps_control_n_bplots, file=file.path(project,"figures/neuromaps/neuromaps_controlCHR_correlations.png"), device = "png", height = 8, width = 9)

}
```

RH case-control neuromaps
```{r neuromapCorRH}
# read data fromm Kuldeep
neuromaps_LR <- read.csv(file.path(project,"df_neuromaps_Glasser_lhrh_360_version2.csv"), header=TRUE) %>% rename("GlasserRegion"="X")
neuromaps_R <- neuromaps_LR[181:360,]

nmap_cols_R <- names(neuromaps_R)[which(names(neuromaps_R) !="GlasserRegion")]

# add size of ROIs
roi_sizes_R <- xii_Ji_parcel$data$cortex_right %>% table %>% as.data.frame
colnames(roi_sizes_R) <- c("INDEX","ROI_size")

# update nmap_cols
nmap_cols_R <- c(nmap_cols_R,"ROI_size")

# function to merge CAB-NP results with HCP parcel names
cabnp_hcp_rh <- function(hcp_df, colname="GlasserRegion", cabnp_df, sizes=roi_sizes_R){
  rh <- filter(cabnp_df, INDEX %in% 181:360)
  rh$GLASSERLABELNAME
  rh[,colname] <- rh$GLASSERLABELNAME %>% gsub("^R_","rh_",.) %>% gsub("_ROI","",.)
  out <- merge(x=rh, y=hcp_df, by=colname)
  out <- merge(x=out, y=sizes, by="INDEX")
  return(out)
}
 
# merge with neuromap
rsfa_22q_nmap_R <- cabnp_hcp_rh(cabnp_df=rsfa_22q_lms, hcp_df=neuromaps_R)
netho_22q_nmap_R <- cabnp_hcp_rh(cabnp_df=netho_22q_lms, hcp_df=neuromaps_R)
gbc_22q_nmap_R <- cabnp_hcp_rh(cabnp_df=gbc_22q_lms, hcp_df=neuromaps_R)

rsfa_chr_nmap_R <- cabnp_hcp_rh(cabnp_df=rsfa_chr_lms, hcp_df=neuromaps_R)
netho_chr_nmap_R <- cabnp_hcp_rh(cabnp_df=netho_chr_lms, hcp_df=neuromaps_R)
gbc_chr_nmap_R <- cabnp_hcp_rh(cabnp_df=gbc_chr_lms, hcp_df=neuromaps_R)

# get neuromap df without fMRI result
neuromaps_ordered_R <- subset(data.table(rsfa_22q_nmap_R), select=-c(group_beta, group_FDR_q, group_FDR_sig, group_beta_FDR, group_se, group_t, group_p))

# # correlate with nmap columns
# nmap_cor <- function(map1, map_all, method="pearson", use="complete.obs", cols=nmap_cols){
#   cor <- lapply(cols, function(c) cor_brain_maps(map1=map1, map2=map_all[,c], method=method, use=use)) %>% as.numeric
#   out <- data.frame(map=cols, cor=cor)
#   out$cor %<>% as.numeric
#   out <- out[order(out$cor),]
#   return(out)
# }
# 
rsfa_22q_nmap_cor_R <- nmap_cor(map1=rsfa_22q_nmap_R$group_beta, map_all=rsfa_22q_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
netho_22q_nmap_cor_R <- nmap_cor(map1=netho_22q_nmap_R$group_beta, map_all=netho_22q_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
gbc_22q_nmap_cor_R <- nmap_cor(map1=gbc_22q_nmap_R$group_beta, map_all=gbc_22q_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)

rsfa_chr_nmap_cor_R <- nmap_cor(map1=rsfa_chr_nmap_R$group_beta, map_all=rsfa_chr_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
netho_chr_nmap_cor_R <- nmap_cor(map1=netho_chr_nmap_R$group_beta, map_all=netho_chr_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
gbc_chr_nmap_cor_R <- nmap_cor(map1=gbc_chr_nmap_R$group_beta, map_all=gbc_chr_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)

# neuromaps permuted p-vals
nmap_match_R <- data.frame(variable=c("cmruglu", "cmr02", "CBF", "cbv", "G1.fMRI","intersubjvar", "meg_delta", "meg_theta", "meg_alpha", "meg_beta", "meg_gamma1", "meg_gamma2","ROI_size"), name=c("Glucose metabolism", "Oxygen metabolism", "Cerebral blood flow", "Cerebral blood volume","fMRI gradient", "Intersubject variability", "MEG delta", "MEG theta", "MEG alpha", "MEG beta", "MEG gamma1", "MEG gamma2","ROI size"))


# 22q
rsfa_22q_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=rsfa_22q_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=rsfa_22q_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

netho_22q_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=netho_22q_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=netho_22q_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

gbc_22q_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=gbc_22q_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=gbc_22q_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

# chr
rsfa_chr_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=rsfa_chr_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=rsfa_chr_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

netho_chr_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=netho_chr_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=netho_chr_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

gbc_chr_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=gbc_chr_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=gbc_chr_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)
```

plot RH 22q case-control neuromaps
```{r plotNeuromap22qRH}
# create long dataframes to plot nulls
rsfa_22q_nuls_long_R <- melt.data.table(as.data.table(rsfa_22q_nmap_p_R$nulls), id.vars="perm")
rsfa_22q_nuls_long_R$variable <- factor(rsfa_22q_nuls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

netho_22q_nuls_long_R <- melt.data.table(as.data.table(netho_22q_nmap_p_R$nulls), id.vars="perm")
netho_22q_nuls_long_R$variable <- factor(netho_22q_nuls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

gbc_22q_nuls_long_R <- melt.data.table(as.data.table(gbc_22q_nmap_p_R$nulls), id.vars="perm")
gbc_22q_nuls_long_R$variable <- factor(gbc_22q_nuls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

# plot
gbc_box_R <- ggplot(data=gbc_22q_nuls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=gbc_22q_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")+
  theme(legend.position="none")

netho_box_R <- ggplot(data=netho_22q_nuls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=netho_22q_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")

rsfa_box_R <- ggplot(data=rsfa_22q_nuls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  #geom_half_violin(fill="grey50", side="r", ="lightgrey", side="r", lty="blank")+
  geom_point(data=rsfa_22q_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  xlab("Brain Map Comparison")+
  #xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match_R$name)

neuromaps_22q_bplots_R <- gbc_box_R/netho_box_R/rsfa_box_R+plot_layout(guides = "collect")
neuromaps_22q_bplots_R

if(save_outputs==TRUE){
  ggsave(neuromaps_22q_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_22q_correlations_rh.pdf"), device = "pdf", height = 8, width = 8)
  ggsave(neuromaps_22q_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_22q_correlations_rh.png"), device = "png", height = 8, width = 8)
}
```

plot RH chr neuromaps
```{r plotNeuromapCHRRH}
# create long dataframes to plot nulls
rsfa_chr_nuls_long_R <- melt.data.table(as.data.table(rsfa_chr_nmap_p_R$nulls), id.vars="perm")
rsfa_chr_nuls_long_R$variable <- factor(rsfa_chr_nuls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

netho_chr_nuls_long_R <- melt.data.table(as.data.table(netho_chr_nmap_p_R$nulls), id.vars="perm")
netho_chr_nuls_long_R$variable <- factor(netho_chr_nuls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

gbc_chr_nuls_long_R <- melt.data.table(as.data.table(gbc_chr_nmap_p_R$nulls), id.vars="perm")
gbc_chr_nuls_long_R$variable <- factor(gbc_chr_nuls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

# plot
chr_gbc_box_R <- ggplot(data=gbc_chr_nuls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=gbc_chr_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","steelblue"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")+
  theme(legend.position="none")

chr_netho_box_R <- ggplot(data=netho_chr_nuls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=netho_chr_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","steelblue"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")+
  theme(legend.position="none")
  
chr_rsfa_box_R <- ggplot(data=rsfa_chr_nuls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  #geom_half_violin(fill="grey50", side="r", ="lightgrey", side="r", lty="blank")+
  geom_point(data=rsfa_chr_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3,alpha=0.5)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  scale_color_manual(values = c("tan","steelblue"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  xlab("Brain Map Comparison")+
  #xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match_R$name)

neuromaps_chr_bplots_R <- chr_gbc_box_R/chr_netho_box_R/chr_rsfa_box_R+plot_layout(guides = "collect")
neuromaps_chr_bplots_R

if(save_outputs==TRUE){
  ggsave(neuromaps_chr_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_chr_correlations_rh.pdf"), device = "pdf", height = 8, width = 8)
  ggsave(neuromaps_chr_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_chr_correlations_rh.png"), device = "png", height = 8, width = 8)
}
```

control RH neuromaps
```{r neuromapCorCtrlRH}

# merge with neuromap
control_22q_gbc_nmap_R   <- cabnp_hcp_rh(cabnp_df=control_22q_gbc_k, hcp_df=neuromaps_R)
control_22q_netho_nmap_R <- cabnp_hcp_rh(cabnp_df=control_22q_netho_k, hcp_df=neuromaps_R)
control_22q_rsfa_nmap_R  <- cabnp_hcp_rh(cabnp_df=control_22q_rsfa_k, hcp_df=neuromaps_R)

control_n_gbc_nmap_R    <- cabnp_hcp_rh(cabnp_df=control_n_gbc_k, hcp_df=neuromaps_R)
control_n_netho_nmap_R  <- cabnp_hcp_rh(cabnp_df=control_n_netho_k, hcp_df=neuromaps_R)
control_n_rsfa_nmap_R   <- cabnp_hcp_rh(cabnp_df=control_n_rsfa_k, hcp_df=neuromaps_R)

# get correlations
control_22q_gbc_nmap_cor_R   <- nmap_cor(map1=control_22q_gbc_nmap_R$value, map_all=control_22q_gbc_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
control_22q_netho_nmap_cor_R <- nmap_cor(map1=control_22q_netho_nmap_R$value, map_all=control_22q_netho_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
control_22q_rsfa_nmap_cor_R  <- nmap_cor(map1=control_22q_rsfa_nmap_R$value, map_all=control_22q_rsfa_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)

control_n_gbc_nmap_cor_R    <- nmap_cor(map1=control_n_gbc_nmap_R$value, map_all=control_n_gbc_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
control_n_netho_nmap_cor_R  <- nmap_cor(map1=control_n_netho_nmap_R$value, map_all=control_n_netho_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)
control_n_rsfa_nmap_cor_R   <- nmap_cor(map1=control_n_rsfa_nmap_R$value, map_all=control_n_rsfa_nmap_R, method="pearson", use="complete.obs", cols=nmap_cols_R)

# get pvals
control_22q_gbc_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=control_22q_gbc_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=gbc_control_22q_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_22q_netho_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=control_22q_netho_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=netho_control_22q_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_22q_rsfa_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=control_22q_rsfa_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=rsfa_control_22q_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_n_gbc_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=control_n_gbc_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=gbc_control_n_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_n_netho_nmap_p_R  <- perm_p_neuromaps(neuromap_outputs=control_n_netho_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=netho_control_n_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

control_n_rsfa_nmap_p_R <- perm_p_neuromaps(neuromap_outputs=control_n_rsfa_nmap_cor_R, neuromap_df=neuromaps_ordered_R, bsmash=rsfa_control_n_bsmash_R, bsmash_cols=paste0("V",1:10000), alternative="two.sided", verbose=FALSE)

```

plot control RH neuromaps results
```{r plotNeuromap22qRH}
# create long dataframes to plot nulls
control_22q_gbc_nulls_long_R <- melt.data.table(as.data.table(control_22q_gbc_nmap_p_R$nulls), id.vars="perm")
control_22q_gbc_nulls_long_R$variable <- factor(control_22q_gbc_nulls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

control_22q_netho_nulls_long_R <- melt.data.table(as.data.table(control_22q_netho_nmap_p_R$nulls), id.vars="perm")
control_22q_netho_nulls_long_R$variable <- factor(control_22q_netho_nulls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

control_22q_rsfa_nulls_long_R <- melt.data.table(as.data.table(control_22q_rsfa_nmap_p_R$nulls), id.vars="perm")
control_22q_rsfa_nulls_long_R$variable <- factor(control_22q_rsfa_nulls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

control_n_gbc_nulls_long_R <- melt.data.table(as.data.table(control_n_gbc_nmap_p_R$nulls), id.vars="perm")
control_n_gbc_nulls_long_R$variable <- factor(control_n_gbc_nulls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

control_n_netho_nulls_long_R <- melt.data.table(as.data.table(control_n_netho_nmap_p_R$nulls), id.vars="perm")
control_n_netho_nulls_long_R$variable <- factor(control_n_netho_nulls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)

control_n_rsfa_nulls_long_R <- melt.data.table(as.data.table(control_n_rsfa_nmap_p_R$nulls), id.vars="perm")
control_n_rsfa_nulls_long_R$variable <- factor(control_n_rsfa_nulls_long_R$variable,levels=nmap_match_R$variable,ordered=TRUE)


# plot
ctrl_22q_gbc_box_R <- ggplot(data=control_22q_gbc_nulls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_22q_gbc_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")
  #theme(legend.position="none")

ctrl_22q_netho_box_R <- ggplot(data=control_22q_netho_nulls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_22q_netho_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")

ctrl_22q_rsfa_box_R <- ggplot(data=control_22q_rsfa_nulls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_22q_rsfa_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match_R$name)


ctrl_n_gbc_box_R <- ggplot(data=control_n_gbc_nulls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_n_gbc_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Global Connectivity")+
  theme(legend.position="none")

ctrl_n_netho_box_R <- ggplot(data=control_n_netho_nulls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_n_netho_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  #theme(axis.text.x = element_text(angle = 45, hjust=1))+
  theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #xlab("Brain Map Comparison")+
  xlab("")+
  ggtitle("Local Connectivity")

ctrl_n_rsfa_box_R <- ggplot(data=control_n_rsfa_nulls_long_R, aes(y=value, x=variable))+
  geom_boxplot(outlier.shape=21, color="grey50", alpha=0.5)+
  geom_point(data=control_n_rsfa_nmap_p_R$pvals,aes(x=map, y=cor, color=p < 0.05, shape=p < 0.05), size=3)+
  scale_color_manual(values = c("tan","red"))+
  scale_shape_manual(values=c(18,16))+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  #theme(axis.text.x = element_blank())+
  ylab("Pearson's r")+
  #ylab("")+
  xlab("Brain Map Comparison")+
  #xlab("")+
  ggtitle("Brain Signal Variability")+
  theme(plot.margin = unit(c(0,0,0,0.7),"in"))+
  scale_x_discrete(labels=nmap_match_R$name)+
  theme(legend.position="none")
 
neuromaps_control_n_bplots_R <- ctrl_n_gbc_box_R/ctrl_n_netho_box_R/ctrl_n_rsfa_box_R+plot_layout(guides = "collect")
neuromaps_control_22q_bplots_R <- ctrl_22q_gbc_box_R/ctrl_22q_netho_box_R/ctrl_22q_rsfa_box_R+plot_layout(guides = "collect")
#neuromaps_control_bplots_R <- ctrl_22q_gbc_box_R/ctrl_n_gbc_box_R/ctrl_22q_netho_box_R/ctrl_n_netho_box_R/ctrl_22q_rsfa_box_R/ctrl_n_rsfa_box_R+plot_layout(guides = "collect")
#neuromaps_control_bplots <- ggarrange(neuromaps_control_22q_bplots, neuromaps_control_n_bplots, nrow=1)

if(save_outputs==TRUE){
  # ggsave(neuromaps_control_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_control_correlations_rh.pdf"), device = "pdf", height = 12, width = 10)
  # ggsave(neuromaps_control_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_control_correlations_rh.png"), device = "png", height = 12, width = 10)

  ggsave(neuromaps_control_22q_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_control22q_correlations_rh.pdf"), device = "pdf", height = 8, width = 8)
  ggsave(neuromaps_control_22q_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_control22q_correlations_rh.png"), device = "png", height = 8, width = 8)

  ggsave(neuromaps_control_n_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_controlCHR_correlations_rh.pdf"), device = "pdf", height = 8, width = 8)
  ggsave(neuromaps_control_n_bplots_R, file=file.path(project,"figures/neuromaps/neuromaps_controlCHR_correlations_rh.png"), device = "png", height = 8, width = 8)
}
```



## Supplemental analyses
collect main effect of site from models
```{r supSite, paged.print=FALSE}
# function to get columns with site p-values (for only regions with FDR significant main effect of group)
get_site_p <- function(df, roicols=c("INDEX","LABEL","HEMISPHERE","NETWORK","NETWORKKEY","GLASSERLABELNAME","group_FDR_sig")){
  cols <- colnames(df)
  # filter for group significance
  gsig <- filter(df, group_FDR_sig==TRUE)
  # get all columns starting with Site and ending with _p
  scols <- grep("Site.*_p",cols, value=TRUE)
  # get all pvals
  sp_all <- gsig[,scols] %>% as.vector() %>% unlist %>% as.numeric()
  # return list object with data frame and vector of all site p-values
  out <- list(df=gsig[,c(roicols,scols)], all_p=sp_all)
  return(out)
}

# get site p-values for each measure
site_p_all <- lapply(list(rsfa_22q_lms, rsfa_chr_lms, netho_22q_lms, netho_chr_lms, gbc_22q_lms, gbc_chr_lms), get_site_p)

# get smallest p-value for each measure
site_p_mins <- lapply(site_p_all, function(s) min(s$all_p))
```

within 22qDel and CHR groups, LM comparing with/without antipsychotic meds
```{r supAPD}
# function to add med status to results dfs, filter for only 22qDel/CHR
add_demo_cols <- function(list, demo, democols=c("Med_Antipsychotic","IQ_full"), idcol="MRI_S_ID"){
  out <- list
  out$df <- merge(x=out$df, y=demo[,c(idcol, democols)], by=idcol)
  return(out)
}
 
# test linear model comparing yes/no meds within patients
rsfa_22q_med <- get_parcel_group_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl), groupcol="Med_Antipsychotic", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("RSFA 22q significant med effects:",sum(rsfa_22q_med$group_FDR_sig)))

rsfa_chr_med <- get_parcel_group_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_napls_all), groupcol="Med_Antipsychotic", groups=c("Y","N"), refgroup="N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CHR")
print(paste("RSFA CHR significant med effects:",sum(rsfa_chr_med$group_FDR_sig)))

netho_22q_med <- get_parcel_group_lm(list=add_demo_cols(list=netho_wide, demo=demo_multisite_bl), groupcol="Med_Antipsychotic", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("NetHo 22q significant med effects:",sum(netho_22q_med$group_FDR_sig)))

netho_chr_med <- get_parcel_group_lm(list=add_demo_cols(list=netho_wide, demo=demo_napls_all), groupcol="Med_Antipsychotic", groups=c("Y","N"), refgroup="N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CHR")
print(paste("NetHo CHR significant med effects:",sum(netho_chr_med$group_FDR_sig)))

gbc_22q_med <- get_parcel_group_lm(list=add_demo_cols(list=gbc_wide, demo=demo_multisite_bl), groupcol="Med_Antipsychotic", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("GBC 22q significant med effects:",sum(gbc_22q_med$group_FDR_sig)))

gbc_chr_med <- get_parcel_group_lm(list=add_demo_cols(list=gbc_wide, demo=demo_napls_all), groupcol="Med_Antipsychotic", groups=c("Y","N"), refgroup="N", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CHR")
print(paste("GBC CHR significant med effects:",sum(gbc_chr_med$group_FDR_sig)))

# get counts
print("22qDel med subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl, democols="Med_Antipsychotic")$df, Group=="22qDel")$Med_Antipsychotic %>% as.factor %>% summary
print("CHR med subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_napls_all, democols="Med_Antipsychotic")$df, Group=="CHR")$Med_Antipsychotic %>% as.factor %>% summary
```

within 22qDel group, LM comparing with/without congenital cardiac Dx (currently missing info for Rome, and unsure of coding for SUNY)
```{r supCardiac}
# exclude rome and SUNY until confirmed
demo_cardiac <- demo_multisite_bl
#demo_cardiac[which(demo_cardiac$Site %in% c("Rome","SUNY")),"cardiac"] <- NA

# get main effects of group for each measure
# TODO: add cardiac status for Rome (currently NA), and confirm SUNY
rsfa_22q_heart <- get_parcel_group_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_cardiac, democols="cardiac"), groupcol="cardiac", groups=c("Y","N"),refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("RSFA 22q significant cardiac effects:",sum(rsfa_22q_heart$group_FDR_sig)))

netho_22q_heart <- get_parcel_group_lm(list=add_demo_cols(list=netho_wide, demo=demo_cardiac, democols="cardiac"), groupcol="cardiac", groups=c("Y","N"),refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("NetHo 22q significant cardiac effects:",sum(netho_22q_heart$group_FDR_sig)))

gbc_22q_heart <- get_parcel_group_lm(list=add_demo_cols(list=gbc_wide, demo=demo_cardiac, democols="cardiac"), groupcol="cardiac", groups=c("Y","N"),refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("GBC 22q significant cardiac effects:",sum(gbc_22q_heart$group_FDR_sig)))

# get counts
print("22qDel cardiac subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_cardiac, democols="cardiac")$df, Group=="22qDel")$cardiac %>% summary

```

psychosis dx relationships in 22q (this is underpowered with only n=16 PS+)
```{r supPsychosisAPD}
# test linear model comparing psychosis dx within patients
rsfa_22q_psych <- get_parcel_group_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl, democols="psych_dx"), groupcol="psych_dx", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("RSFA 22q significant psychosis effects:",sum(rsfa_22q_psych$group_FDR_sig)))

netho_22q_psych <- get_parcel_group_lm(list=add_demo_cols(list=netho_wide, demo=demo_multisite_bl, democols="psych_dx"), groupcol="psych_dx", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("NetHo 22q significant psychosis effects:",sum(netho_22q_psych$group_FDR_sig)))

gbc_22q_psych <- get_parcel_group_lm(list=add_demo_cols(list=gbc_wide, demo=demo_multisite_bl, democols="psych_dx"), groupcol="psych_dx", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("GBC 22q significant psychosis effects:",sum(gbc_22q_psych$group_FDR_sig)))

# get counts
print("22qDel PS+/PS- subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl, democols="psych_dx")$df, Group=="22qDel")$psych_dx %>% as.factor %>% summary
```
repeat adding antipsychotic as covar
```{r supPsychosisAPD}
# test linear model comparing psychosis dx within patients
rsfa_22q_psych <- get_parcel_group_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl, democols=c("psych_dx","Med_Antipsychotic")), covars="AGE + AGE2 + SEX + Site + percent_udvarsme + Med_Antipsychotic", groupcol="psych_dx", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("RSFA 22q significant psychosis effects:",sum(rsfa_22q_psych$group_FDR_sig)))

netho_22q_psych <- get_parcel_group_lm(list=add_demo_cols(list=netho_wide, demo=demo_multisite_bl, democols=c("psych_dx","Med_Antipsychotic")), covars="AGE + AGE2 + SEX + Site + percent_udvarsme + Med_Antipsychotic", groupcol="psych_dx", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("NetHo 22q significant psychosis effects:",sum(netho_22q_psych$group_FDR_sig)))

gbc_22q_psych <- get_parcel_group_lm(list=add_demo_cols(list=gbc_wide, demo=demo_multisite_bl, democols=c("psych_dx","Med_Antipsychotic")), covars="AGE + AGE2 + SEX + Site + percent_udvarsme + Med_Antipsychotic", groupcol="psych_dx", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("GBC 22q significant psychosis effects:",sum(gbc_22q_psych$group_FDR_sig)))

# get percent antipsychotic use by group
PsychAPD22q <- CreateTableOne(vars="Med_Antipsychotic", strata="psych_dx", data=filter(demo_multisite_bl, Group=="22qDel"))
PsychAPD22q
```
investigate psychosis GBC effect in 22q further (only 16 people with psychosis though)
```{r supPsychosisCont}
# get significant regions
psych_22q_gbc_sig <- filter(gbc_22q_psych, group_FDR_sig==TRUE)

# get actual models for each to confirm everything looks good
psych_22q_gbc_mods <-lapply(psych_22q_gbc_sig$indexcol, function(i) summary(lm_parcel_group_covars(df=filter(add_demo_cols(list=gbc_wide, demo=demo_multisite_bl, democols="psych_dx")$df, Group=="22qDel"), var=i,predictors="psych_dx + AGE + AGE2 + SEX + Site + percent_udvarsme", groupcol="psych_dx", groups=c("Y","N"), refgroup="N", test_out_model=TRUE)))

# plot
pl_gbc_22q_psych_fdrb <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=gbc_22q_psych, roi_col="INDEX", val_col="group_beta_FDR")
view_xifti_surface(pl_gbc_22q_psych_fdrb, title="Global Connectivity: 22qDel PS+ vs PS- (FDR q<0.05)", cex.title=1.3,zlim=c(-1.3,1.3), colors=pal_red_blue())
if(save_outputs==TRUE){
  view_xifti_surface(pl_gbc_22q_psych_fdrb,zlim=c(-1.3,1.3), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/gbc_22qPS_b_fdr.png"),legend_embed=TRUE)
}

pl_gbc_22q_psych_b <- atlas_xifti_new_vals(xii=xii_Ji_parcel, df=gbc_22q_psych, roi_col="INDEX", val_col="group_beta")
view_xifti_surface(pl_gbc_22q_psych_b, title="Global Connectivity: 22qDel PS+ vs PS- ", cex.title=1.3,zlim=c(-1.3,1.3), colors=pal_red_blue())
if(save_outputs==TRUE){
  view_xifti_surface(pl_gbc_22q_psych_b,zlim=c(-1.3,1.3), colors=pal_red_blue(), fname=file.path(project,"figures/fmri_maps/gbc_22qPS_b.png"),legend_embed=TRUE)
}
```

lm of IQ in each group
```{r supIQ}
# function to return beta coefficient for a continuous predictor (edit of lm_parcel_group_covars)   
lm_parcel_bhv_covars <- function(df, var, predictors, statname="IQ_full"){
  # create formula with var on left side and predictors string on right
  form <- reformulate(predictors,response=var)
  # test linear model
  lm <- lm(formula=form,data=df, na.action="na.omit")
  slm <- summary(lm)
  out <- slm$coefficients[statname,] %>% t %>% as.data.frame
  colnames(out) <- paste0(statname,c("_beta","_se","_t","_p"))
  return(out)
}
#test <- lm_parcel_bhv_covars(df=filter(add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl)$df, Group %in% c("22qDel")), var="r_1",predictors="IQ_full + SEX + Site + percent_udvarsme") 

# function to apply lm at each parcel, expects list object output from rows_to_cols
get_parcel_bhv_lm <- function(list,
                                sitecol="Site",
                                refsite,
                                covars="SEX + Site + percent_udvarsme", 
                                alpha=0.05, 
                                roi_key=ji_key,
                                prefix="r_",
                                filter=FALSE,
                                filtercol="",
                                filterin="",
                                statname="IQ_full"){
  # add group to string of model variables
  predictors <- paste(statname, "+", covars)
  # filter by specified groups and relevel factor
  df_all <- as.data.frame(list$df)
  # filter data based to keep only rows wither value of filtercol is in filterin
  if(filter==TRUE){
    df <- df_all %>% filter(.data[[filtercol]] %in% filterin)
  }else{
    df <- df_all
  }
  # relevel site
  df[,sitecol] <- relevel(as.factor(df[,sitecol]), ref=refsite)
  # do linear model for every parcel, FDR correct p-values, and create column of betas set to NA when not FDR significant
  parc_cols <- list$parcels
  stats <- lapply(parc_cols, function(v) lm_parcel_bhv_covars(var=v, df=df, predictors=predictors, statname=statname)) %>% do.call(rbind,.) %>% as.data.frame
  stats$indexcol <- parc_cols
  stats$INDEX <- gsub(prefix,"",stats$indexcol)
  stats[,paste0(statname,"_FDR_q")] <- p.adjust(stats[,paste0(statname,"_p")], method="fdr")
  stats[,paste0(statname,"_FDR_sig")] <- stats[,paste0(statname,"_FDR_q")] < alpha
  out <- merge(x=roi_key, y=stats, by="INDEX", all.x=TRUE, all.y=TRUE)
  return(out)
}

# get IQ relationships within a given group
# BSV
rsfa_22q_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("RSFA 22q significant IQ effects:",sum(rsfa_22q_iq$IQ_full_FDR_sig)))

rsfa_ctrl22q_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CONTROL")
print(paste("RSFA Control-22q significant IQ effects:",sum(rsfa_ctrl22q_iq$IQ_full_FDR_sig)))

rsfa_chr_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_napls_all), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CHR")
print(paste("RSFA CHR significant IQ effects:",sum(rsfa_chr_iq$IQ_full_FDR_sig)))

rsfa_ctrlchr_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_napls_all), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CONTROL-N")
print(paste("RSFA Control-CHR significant IQ effects:",sum(rsfa_ctrlchr_iq$IQ_full_FDR_sig)))

# LC
netho_22q_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=netho_wide, demo=demo_multisite_bl), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")

netho_ctrl22q_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=netho_wide, demo=demo_multisite_bl), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CONTROL")
print(paste("NetHo 22q significant IQ effects:",sum(netho_ctrl22q_iq$IQ_full_FDR_sig)))

netho_chr_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=netho_wide, demo=demo_napls_all), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CHR")
print(paste("NetHo CHR significant IQ effects:",sum(netho_chr_iq$IQ_full_FDR_sig)))

netho_ctrlchr_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=netho_wide, demo=demo_napls_all), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CONTROL-N")
print(paste("NetHo Control-CHR significant IQ effects:",sum(netho_ctrlchr_iq$IQ_full_FDR_sig)))

# GBC
gbc_22q_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=gbc_wide, demo=demo_multisite_bl), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("GBC 22q significant IQ effects:",sum(gbc_22q_iq$IQ_full_FDR_sig)))

gbc_ctrl22q_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=gbc_wide, demo=demo_multisite_bl), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CONTROL")
print(paste("GBC Control-22q significant IQ effects:",sum(gbc_ctrl22q_iq$IQ_full_FDR_sig)))

gbc_chr_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=gbc_wide, demo=demo_napls_all), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CHR")
print(paste("GBC CHR significant IQ effects:",sum(gbc_chr_iq$IQ_full_FDR_sig)))

gbc_ctrlchr_iq <- get_parcel_bhv_lm(list=add_demo_cols(list=gbc_wide, demo=demo_napls_all), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CONTROL-N")
print(paste("GBC Control-CHR significant IQ effects:",sum(gbc_ctrlchr_iq$IQ_full_FDR_sig)))

# get counts
print("22qDel IQ subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl, democols="IQ_full")$df, Group=="22qDel" & !is.na(IQ_full))$IQ_full %>% length
print("Control22q IQ subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_multisite_bl, democols="IQ_full")$df, Group=="CONTROL" & !is.na(IQ_full))$IQ_full %>% length
print("CHR IQ subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_napls_all, democols="IQ_full")$df, Group=="CHR" & !is.na(IQ_full))$IQ_full %>% length
print("ControlCHR IQ subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_napls_all, democols="IQ_full")$df, Group=="CONTROL-N" & !is.na(IQ_full))$IQ_full %>% length
```

get SIPS/PANSS subthreshold PS group in 22qDel
```{r supSIPS}
# read UCLA SIPS
ucla_sips <- read.csv(file.path(project,"demographics/ucla_sistat/Re22Q_Form_SIPS.csv"), na.strings = c(".","","-9999","-9998"),strip.white =T)
ucla_demo <- read.csv(file.path(project,"demographics/ucla_sistat/Re22Q_Qry_demo_mri.csv"), na.strings = c(".","","-9999","-9998"),strip.white =T)

# function to get psychosis status from SIPS
# to be applied to the row indices of a demographics df, and also given the SIPS df
get_sips <- function(r, demo, sips){
   mri_id <- demo$MRI_S_ID[[r]]
   sub <- demo$SUBJECTID[[r]]
   visit <- demo$CONVERTEDVISITNUM[[r]]
   df_out <- data.frame(MRI_S_ID=mri_id, SUBJECTID=sub, CONVERTEDVISITNUM=visit)
   sips_sesh <- sips %>% filter(SUBJECTID == sub & CONVERTEDVISITNUM == visit)
   if(nrow(sips_sesh) < 1){
     # if no match for sub+visit in sips table, set outputs to NA
     df_out[, c("SIPS_p_sum", "SIPS_n_sum", "SIPS_d_sum", "SIPS_g_sum", "SIPS_total", "SIPS_psychosis_6", "SIPS_psspectrum_3")] <- rep(NA, times = 7)
   }else if(nrow(sips_sesh) > 1){
     # if more than one match for sub+visit, note error
     df_out[, c("SIPS_p_sum", "SIPS_n_sum", "SIPS_d_sum", "SIPS_g_sum", "SIPS_total", "SIPS_psychosis_6", "SIPS_psspectrum_3")] <- rep("ERROR-duplicates", times = 7)
   }else{
     # get SIPS P scores
     sips_p_scores <- sips_sesh[c("P1SEV", "P2SEV", "P3SEV", "P4SEV", "P5SEV")]
     # sum SIPS P
     df_out[,"SIPS_p_sum"] <- sum(sips_p_scores)
     # get SIPS N
     sips_n_scores <- sips_sesh[c("N1SEV", "N2SEV", "N3SEV", "N4SEV", "N5SEV", "N6SEV")]
     df_out[,"SIPS_n_sum"] <- sum(sips_n_scores)
     # get SIPS D
     sips_d_scores <- sips_sesh[c("D1SEV", "D2SEV", "D3SEV", "D4SEV")]
     df_out[,"SIPS_d_sum"] <- sum(sips_d_scores)
     # get SIPS G
     sips_g_scores <- sips_sesh[c("G1SEV", "G2SEV", "G3SEV", "G4SEV")]
     df_out[,"SIPS_g_sum"] <- sum(sips_g_scores)
     # get SIPS total
     df_out["SIPS_total"] <- (df_out["SIPS_p_sum"] +  df_out["SIPS_n_sum"] +  df_out["SIPS_d_sum"] +  df_out["SIPS_g_sum"] )
     # check psychosis criteria of at least one SIPS P score of 6
     count_6 <- length(which(sips_p_scores == 6))
     if(is.na(sum(sips_p_scores))){
       df_out[,"SIPS_psychosis_6"] <- NA
     }else if(count_6 > 0){
       df_out[,"SIPS_psychosis_6"] <- 1
     }else{
       df_out[,"SIPS_psychosis_6"] <- 0
     }
     # check psychosis-spectrum criteria of at least one SIPS P >= 3
     count_3 <- length(which(sips_p_scores >= 3))
     if(is.na(sum(sips_p_scores))){
       df_out[,"SIPS_psspectrum_3"] <- NA
     }else if(count_3 > 0){
       df_out[,"SIPS_psspectrum_3"] <- 1
     }else{
       df_out[,"SIPS_psspectrum_3"] <- 0
     }
   }
   return(df_out)
}

# get sips 
ucla_demo_sips <- lapply(1:nrow(ucla_demo), function(r) get_sips(r = r, demo=ucla_demo, sips = ucla_sips)) %>% do.call(rbind,.) %>% filter(!is.na(MRI_S_ID)) %>% filter(!MRI_S_ID %in% c("NO SCAN", "EXCLUDED"))

# read IoP SIPS
iop_sips <- read_xlsx(file.path(project,"demographics/22Qiop_SIPS.xlsx"), na = c(".","","-9999","-9998"),trim_ws =TRUE)

# function to get psychosis status from SIPS
# to be applied to the row indices of a demographics df, and also given the SIPS df
get_sips_iop <- function(r, demo, sips){
   mri_id <- demo$MRI_S_ID[[r]]
   sub <- demo$SUBJECTID[[r]]
   df_out <- data.frame(MRI_S_ID=mri_id, SUBJECTID=sub)
   sips_sesh <- sips %>% filter(SUBJECTID == sub )
   if(nrow(sips_sesh) < 1){
     # if no match for sub+visit in sips table, set outputs to NA
     df_out[, c("SIPS_p_sum", "SIPS_n_sum", "SIPS_d_sum", "SIPS_g_sum", "SIPS_total", "SIPS_psychosis_6", "SIPS_psspectrum_3")] <- rep(NA, times = 7)
   }else if(nrow(sips_sesh) > 1){
     # if more than one match for sub+visit, note error
     df_out[, c("SIPS_p_sum", "SIPS_n_sum", "SIPS_d_sum", "SIPS_g_sum", "SIPS_total", "SIPS_psychosis_6", "SIPS_psspectrum_3")] <- rep("ERROR-duplicates", times = 7)
   }else{
     # get SIPS P scores
     sips_p_scores <- sips_sesh[c("p1sev", "p2sev", "p3sev", "p4sev", "p5sev")]
     # sum SIPS P
     df_out[,"SIPS_p_sum"] <- sum(sips_p_scores)
     # get SIPS N
     sips_n_scores <- sips_sesh[c("N1sev", "N2sev", "N3sev", "N4sev", "N5sev", "N6sev")]
     df_out[,"SIPS_n_sum"] <- sum(sips_n_scores)
     # get SIPS D
     sips_d_scores <- sips_sesh[c("D1sev", "D2sev", "D3sev", "D4sev")]
     df_out[,"SIPS_d_sum"] <- sum(sips_d_scores)
     # get SIPS G
     sips_g_scores <- sips_sesh[c("G1sev", "G2sev", "G3sev", "G4sev")]
     df_out[,"SIPS_g_sum"] <- sum(sips_g_scores)
     # get SIPS total
     df_out["SIPS_total"] <- (df_out["SIPS_p_sum"] +  df_out["SIPS_n_sum"] +  df_out["SIPS_d_sum"] +  df_out["SIPS_g_sum"] )
     # check psychosis criteria of at least one SIPS P score of 6
     count_6 <- length(which(sips_p_scores == 6))
     if(is.na(sum(sips_p_scores))){
       df_out[,"SIPS_psychosis_6"] <- NA
     }else if(count_6 > 0){
       df_out[,"SIPS_psychosis_6"] <- 1
     }else{
       df_out[,"SIPS_psychosis_6"] <- 0
     }
     # check psychosis-spectrum criteria of at least one SIPS P >= 3
     count_3 <- length(which(sips_p_scores >= 3))
     if(is.na(sum(sips_p_scores))){
       df_out[,"SIPS_psspectrum_3"] <- NA
     }else if(count_3 > 0){
       df_out[,"SIPS_psspectrum_3"] <- 1
     }else{
       df_out[,"SIPS_psspectrum_3"] <- 0
     }
   }
   return(df_out)
}

# get sips 
iop_demo_sips <- lapply(1:nrow(demo_multisite_bl), function(r) get_sips_iop(r = r, demo=demo_multisite_bl, sips = iop_sips)) %>% do.call(rbind,.)

# read SUNY SIPS
suny_sips <- read_xlsx(file.path(project,"demographics/SUNY_T4_SIPS.xlsx"), na = c(".","","-9999","-9998"),trim_ws =TRUE)
suny_sips_n <- suny_sips[,c("SUBJECT#", "Unusual thought content/delusional ideas", "Suspicious/Persecutory ideas", "Grandiose ideas", "Perceptual abnormalities/hallucinations", "Disorganized communication")]
sips_p_names <- c("P1SEV", "P2SEV", "P3SEV", "P4SEV", "P5SEV")
colnames(suny_sips_n) <- c("SUBJECTID", sips_p_names)
suny_sips_n$MRI_S_ID <- gsub("S","X",suny_sips_n$SUBJECTID)
suny_sips_n$SIPS_psspectrum_3 <- NA
for(r in 1:nrow(suny_sips_n)){
  count_3 <- length(which(suny_sips_n[r,sips_p_names] >= 3))
  if(is.na(sum(suny_sips_n[r,sips_p_names]))){
    suny_sips_n[r,"SIPS_psspectrum_3"] <- NA
  }else if(count_3 > 0){
    suny_sips_n[r,"SIPS_psspectrum_3"] <- 1
  }else{
    suny_sips_n[r,"SIPS_psspectrum_3"] <- 0
  }
}

# combine all SIPS
all_SIPS_22q <- rbind(filter(ucla_demo_sips, !is.na(SIPS_psspectrum_3))[,c("MRI_S_ID","SIPS_psspectrum_3")],
                  filter(iop_demo_sips, !is.na(SIPS_psspectrum_3))[,c("MRI_S_ID","SIPS_psspectrum_3")],
                  filter(suny_sips_n, !is.na(SIPS_psspectrum_3))[,c("MRI_S_ID","SIPS_psspectrum_3")])
all_SIPS_22q$psychosis_risk <- all_SIPS_22q$SIPS_psspectrum_3

# merge with demographics
all_SIPS_22q_demo <- merge(x=all_SIPS_22q, y=demo_multisite_bl, by="MRI_S_ID", all.x=FALSE, all.y=TRUE) 

# calculate percentage of 22qDel meeting criteria for SIPS
count_psrisk <- sum(filter(all_SIPS_22q_demo, Group=="22qDel")$SIPS_psspectrum_3, na.rm = TRUE)
count_0 <- sum((filter(all_SIPS_22q_demo, Group=="22qDel")$SIPS_psspectrum_3 == 0), na.rm = TRUE)
count_na <- sum(is.na(filter(all_SIPS_22q_demo, Group=="22qDel")$SIPS_psspectrum_3), na.rm = TRUE)
frac_22q_psrisk <- count_psrisk/(count_psrisk + count_0 + count_na)
frac_22q_psrisk_nona <- count_psrisk/(count_psrisk + count_0)
# 0.2743902
# 0.323741

# read Rome PANSS
rome_PANSS <- read_xlsx(file.path(project,"demographics/ENIGMA_27_FEB_22_ROME.xlsx"), na = c(".","","-9999","-9998"),trim_ws =TRUE)
rome_PANSS$MRI_S_ID <- rome_PANSS$SubjID
rome_PANSS$PANSS_PS %<>% as.numeric
#hist(rome_PANSS$PANSS_PS)
# get threshold for PANSS that would give same percentile of people as SIPS cutoff excluding NAs (i.e., top 32%)
panss_cut <- quantile(rome_PANSS$PANSS_PS, prob=(1-0.32), na.rm = TRUE)
rome_PANSS$psychosis_risk <- rome_PANSS$PANSS_PS >= panss_cut

# combine all
psrisk_22q_all <- rbind(all_SIPS_22q[,c("MRI_S_ID","psychosis_risk")],
                        rome_PANSS[,c("MRI_S_ID","psychosis_risk")])
# set NA to zero and convert to Y/N factor
psrisk_22q_all[which(is.na(psrisk_22q_all$psychosis_risk)),"psychosis_risk"] <- 0
psrisk_22q_all$psychosis_risk <- factor(psrisk_22q_all$psychosis_risk, levels=c(0,1), labels=c("N","Y"))

# ensure all with official psychosis dx are labeled as Y for psychosis_risk
psrisk_22q_all[which(psrisk_22q_all$MRI_S_ID %in% filter(demo_multisite, psych_dx=="Y")$MRI_S_ID),"psychosis_risk"] <- "Y"

# merge with demo
demo_22q_psrisk <- merge(x=demo_multisite_bl, y=psrisk_22q_all, by="MRI_S_ID", all.x=TRUE, all.y=FALSE)

```

lm of psychosis risk in 22q
```{r supPSrisk}
# test linear model comparing psychosis dx within patients
rsfa_22q_psrisk <- get_parcel_group_lm(list=add_demo_cols(list=rsfa_wide, demo=demo_22q_psrisk, democols="psychosis_risk"), groupcol="psychosis_risk", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("RSFA 22q significant psychosis risk effects:",sum(rsfa_22q_psrisk$group_FDR_sig)))

netho_22q_psrisk <- get_parcel_group_lm(list=add_demo_cols(list=netho_wide, demo=demo_22q_psrisk, democols="psychosis_risk"), groupcol="psychosis_risk", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("NetHo 22q significant psychosis risk effects:",sum(netho_22q_psrisk$group_FDR_sig)))

gbc_22q_psrisk <- get_parcel_group_lm(list=add_demo_cols(list=gbc_wide, demo=demo_22q_psrisk, democols="psychosis_risk"), groupcol="psychosis_risk", groups=c("Y","N"), refgroup="N", refsite="UCLAtrio", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="22qDel")
print(paste("GBC 22q significant psychosis risk effects:",sum(gbc_22q_psrisk$group_FDR_sig)))

# get counts
print("22qDel psychosis risk subject counts:")
filter(add_demo_cols(list=rsfa_wide, demo=demo_22q_psrisk, democols="psychosis_risk")$df, Group=="22qDel")$psychosis_risk %>% as.factor %>% summary

# make new column with proper labels to compare psrisk to controls (Y=22qDel with psychosis risk, N=22qDel without, C=Control22q)
demo_22q_psrisk$psrisk_td <- demo_22q_psrisk$psychosis_risk %>% as.character
demo_22q_psrisk[which(demo_22q_psrisk$Group =="CONTROL"),"psrisk_td"] <- "C"
demo_22q_psrisk$psrisk_td %<>% as.factor


```

overlap of significant CHR LC with 22q LC
```{r lcOverlap}
# get labels of significant LC regions
lc_chr_sig <- filter(netho_chr_lms, group_FDR_sig==TRUE)$LABEL
lc_22q_sig <- filter(netho_22q_lms, group_FDR_sig==TRUE)$LABEL

# proportion of CHR in 22q
sum(lc_chr_sig %in% lc_22q_sig)
length(lc_chr_sig)
sum(lc_chr_sig %in% lc_22q_sig)/length(lc_chr_sig)
lc_chr_sig[which(lc_chr_sig %in% lc_22q_sig)]
```

lm of SIPS positive for regions with significant CHR effect on LC
```{r supSIPSCHR}
# add a sips positive column for demo_napls_all
# sips # TODO read sips
# demo_napls_sips <- merge(x=demo_napls_all, y=sips, by="MRI_S_ID")
# 
# netho_chr_sipsp <- get_parcel_bhv_lm(list=add_demo_cols(list=netho_wide, demo=demo_napls_sips), statname="IQ_full", covars="SEX + Site + percent_udvarsme", refsite="NAPLS1", roi_key=filter(ji_key,INDEX %in% 1:360), filter=TRUE, filtercol="Group", filterin="CHR")

```

demo tables for each site
```{r supDemo, message=FALSE, warning=FALSE, paged.print=FALSE}
# function to create demo table for a given site
make_demo_site <- function(data, site, strata="Group", vars=c("AGE","SEX"), rownames=c("n", "Age, Years, Mean (SD)", "Sex, Female, n (%)")){
  df <- filter(data, Site==site)
  demo_table <- CreateTableOne(data=df, strata=strata, vars=vars)
  demo_table_f <- print(demo_table, showAllLevels = F, test=T,quote=F, contDigits=1) %>% as.data.frame
  rownames(demo_table_f) <- rownames
  site <- data.frame(Site=c(site,rep("", times=length(vars))))
  rownames_df <- data.frame(Demographics=rownames)
  demo_table_s <- cbind(site,rownames_df,demo_table_f[,1:3])
  rownames(demo_table_s) <- NULL

  return(demo_table_s)
}

site_demo_22q <- lapply(c("UCLAtrio", "UCLAprisma", "SUNY", "Rome", "IoP"),function(s) make_demo_site(site=s, data=demo_multisite_bl)) %>% do.call(rbind,.) %>% as.data.frame
site_demo_22q$Site <- gsub("IoP","KCL",site_demo_22q$Site)

site_demo_napls <- lapply(unique(demo_napls_all$Site),function(s) make_demo_site(site=s, data=demo_napls_all)) %>% do.call(rbind,.) %>% as.data.frame
site_demo_napls$Site <- gsub("NAPLS","0",site_demo_napls$Site)

# use gt() to make table for export
# instructions for bolding specific headers https://gt.rstudio.com/reference/tab_style.html
site_demo_22q_out <- site_demo_22q %>% gt(rownames_to_stub=FALSE) %>%
  tab_style(style = cell_text(weight = "bold"),locations = list(cells_column_labels())) %>%
  tab_options(data_row.padding = px(1)) %>%
  cols_align(align="right", columns=everything())

site_demo_napls_out <- site_demo_napls %>% gt(rownames_to_stub=FALSE) %>%
  tab_style(style = cell_text(weight = "bold"),locations = list(cells_column_labels())) %>%
  tab_options(data_row.padding = px(1)) %>%
  cols_align(align="right", columns=everything())

if(save_outputs==TRUE){
   gtsave(site_demo_22q_out, filename = file.path(project,"figures/demographics/supplemental_22q_sites.png"))
   gtsave(site_demo_napls_out, filename = file.path(project,"figures/demographics/supplemental_napls_sites.png"))

}
```

save workspace with main data
```{r paged.print=FALSE}
# save image
if(save_outputs==TRUE){
  save.image(file=file.path(project,"git_exclude/22q_chr_fmri_full_R1.Rdata"),compress = "gzip")
}
```